---
title: "Fig.2 & Fig.S8_Beta_dispersion"
author: "Huanhuan Zhu"
date: "2024-09-25"
output: html_document
---

```{r,fig.align='center', fig.height=4, fig.width=6}
#############################Fig.2 & Fig.S8_Beta_dispersion##########################

library(vegan)
library(betapart)
library(agricolae)
library(ggplot2)
library(patchwork)


### 1. AMF-Bray
rm(list=ls())
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/AMF/otu")

# Reading OTU table
otu_all0 <- read.csv("otu_amfFlattening.csv",check.names = F,row.names = 1,header = T)
otu_all0 <- as.data.frame(t(otu_all0))

# Read metadata file
group0 <- read.csv("sample_metadata.csv",header = T)
group0 <- na.omit(group0)
group <- group0[order(group0$sample.id),]
otu_all0$sample.id <- rownames(otu_all0)
identical(otu_all0$sample.id,group$sample.id)
otu_all <- merge(otu_all0,group,by= "sample.id")

dis <- vegdist(decostand(otu_all[,2:671],"hellinger"), method = 'bray')
mod <- betadisper(d = dis, group = factor(otu_all$plants), type = 'centroid')

#mod
#print(anova(mod));TukeyHSD(mod);TukeyHSD(mod)

p <- adonis2(dis~otu_all$plants)
print(p)

# (1) old betadispersion
plotcol <- c('red','orange',"#20B2AA",'blue',"#581845")

#pdf("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/AMF/otu/Betadisper/AMF-Betadisper-PCoA.pdf",height = 4,width=4)
mar=c(0.5, 0.5, 0.5, 0.5)

plot(mod, col=plotcol,hull = FALSE,cex = 1,label.cex = 0.6,
     main="",xlab="PC1", ylab="PC2",sub="Bray",seg.col=plotcol)
title(paste0("AMF-Betadispersion"),cex =0.8, font =2,line = 2)
mtext(side = 3, sprintf("Adonis: F = %.3f; P = %.3f", p$F[1],p$`Pr(>F)`[1]), 
      col="red", cex =0.6, font =2,line = 0.8)
mtext(side = 3, sprintf("Betadisper: F = %.3f; P = %.3f",anova(mod)$`F value`[1], anova(mod)$`Pr(>F)`[1]), 
      col="red", cex =0.6, font =2,line = 0)

#dev.off()

# (2) new betadispersion & PCoA
df <- data.frame(mod$distances,mod$group)

# Nonparametric test
ST <- kruskal(mod$distances,mod$group, p.adj = "fdr")

# Extracting Chi square value and P value from the result
statis <- as.data.frame(rbind(ST$statistics[,1:2]))

# Creating dataframe for Chi square value and P value
# Sprintf for pasting texts and values
# asterisk (*) among elements represent pasting without space, tilde (~) among elements represent pasting witht space
rp.value <- data.frame(
  label=sprintf("P = %.3e (χ² = %.3g)", 
                statis$p.chisq,statis$Chisq),
  x = "Tamarix chinensis",
  y=0.38)

# Extracting multiple comparision result
statis1 <- as.data.frame(rbind(ST$groups))
# Extracting mean of Nonparametric tests
statis2 <- as.data.frame(rbind(ST$means))

# Extracting Ymax for add letters of multiple comparision?
p1 <- ggplot(df, aes(y=mod.distances, x = factor(mod.group))) +
  stat_boxplot(geom = "errorbar", width=0.3) +
  geom_boxplot(width = 0.5)
ymaxdata <- layer_data(p1) 
statis2$ymax <- ymaxdata$ymax

# Merging dataframe of multiple comparision result with dataframe of mean of nonparametric tests
statis1$id <- rownames(statis1)
statis2$id <- rownames(statis2)
statis2 <- merge(statis2, statis1, by = "id")

# Creating dataframe of geom_text for letters of nonparametric tests
multcomp.data <- data.frame(
  abc = factor(statis2$groups),
  x     = statis2$id,
  y     = as.numeric(statis2$ymax))

# Plot
p2_amf <- ggplot(df, aes(y=mod.distances, x = factor(mod.group, levels = c("Bare land","Suaeda","Tamarix chinensis","Cotton","Maize")))) +
  stat_boxplot(geom = "errorbar", width=0.3) +
  geom_boxplot(width = 0.5) +
  #geom_jitter(size = 0.8) +
  labs(x = "Habitat", y= "Distance to centroid", title = "AMF-Betadispersion") +
  scale_x_discrete(labels = c(
    'Bare land' = "Bareland", 
    'Cotton' = "Cotton", 
    'Maize' = "Maize", 
    'Suaeda' = "Suaeda",
    'Tamarix chinensis' = "Tamarix")) +
  geom_text(
    data  = rp.value, mapping = aes(x = x, y = y, label = label),parse = F,  col="red", hjust = 0.5, size = 5) + 
  geom_text(data = multcomp.data, aes(x = x,y = y+0.02,label=abc),
            color = "black",
            size = 6, hjust = 0.5) +
  theme_bw() +
  ylim(0.2,0.4) +
  theme(panel.grid = element_blank(), 
        axis.ticks.y = element_line(color = "black",linewidth = 0.5)) +
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
        axis.title = element_text(size = 16, face = "bold"),
        axis.title.x = element_blank(),
        axis.text = element_text(size = 12, face = "bold",color = "black"))
p2_amf
#ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/AMF/otu/Betadisper/AMF-Betadisper-Boxplot.pdf", p2_amf, height = 4,width=4.5)

# Boxplot for betadispersion
newplot <- function(title, path){   
  df1 <- data.frame(PCoA1=mod$vectors[,1], PCoA2=mod$vectors[,2], Habitat=mod$group)
  centroid1 <- aggregate(df1$PCoA1~df1$Habitat,FUN="mean")
  centroid2 <- aggregate(df1$PCoA2~df1$Habitat,FUN="mean")
  
  centroid <- merge(centroid1,centroid2,by="df1$Habitat")
  names(centroid) <- c("Habitat","PCoA1","PCoA2")
  subtitle_text <- paste(
    sprintf("Adonis: F = %.3f; P = %.3e", p$F[1], p$`Pr(>F)`[1]),
    sprintf("Betadispersion: F = %.3f; P = %.3e", anova(mod)$`F value`[1], anova(mod)$`Pr(>F)`[1]),
    sep = "\n")
  
  p3 <<- ggplot(df1, aes(PCoA1,PCoA2,color = factor(Habitat,levels = c("Bare land","Suaeda","Tamarix chinensis","Cotton","Maize")))) +
    geom_point(size = 5, alpha=0.5) +
    geom_segment(data = merge(df1, centroid, by = "Habitat"), 
                 aes(x = PCoA1.x, y = PCoA2.x, xend = PCoA1.y, yend = PCoA2.y),alpha=0.5) +
    scale_colour_manual(
      name = "Habitat",
      label = c(
        'Bare land'='Bareland',
        'Cotton'='Cotton',
        'Maize'='Maize',
        'Suaeda'='Suaeda',
        'Tamarix chinensis'='Tamarix'), 
      values = c("red","blue","purple","darkgreen","deepskyblue"),
      guide=guide_legend(override.aes=list(shape = 16))) +
    labs(title = title,subtitle = subtitle_text) +
    theme_bw() +
    theme(
      plot.title = element_text(size = 20, face = "bold",hjust = 0.5), 
      plot.subtitle = element_text(color = "red", size = 12, face = "bold",  hjust = 0.5), 
      legend.title = element_text(colour = "black", size = 15, face = "bold"),
      legend.text = element_text(colour = "black", size = 12, face = "bold"),
      axis.text = element_text(colour = "black", size = 12, face = "bold"),
      axis.title = element_text(colour = "black", size = 15, face = "bold")) 
  
  print(p3)
  #ggsave(path, p2, height = 4,width=6)
}

# (3) boxplot of  betadispersion
newplot("AMF-Betadispersion","E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/AMF/otu/Betadisper/AMF-Betadisper-PCoA-new.pdf")
p3_amf <- p3


### 2. Bacteria-Bray
rm(list=setdiff(ls(), c("newplot", "p2_amf", "p3_amf")))
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Bacteria/otu")

# Reading OTU table
otu_all0 <- read.csv("otu_bacteriaFlattening.csv",check.names = F,row.names = 1,header = T)
otu_all0 <- as.data.frame(t(otu_all0))

# Read metadata file
group0 <- read.csv("sample_metadata.csv",header = T)
group0 <- na.omit(group0)
group <- group0[order(group0$sample.id),]
otu_all0$sample.id <- rownames(otu_all0)
identical(otu_all0$sample.id,group$sample.id)
otu_all <- merge(otu_all0,group,by= "sample.id")

dis <- vegdist(decostand(otu_all[,2:1924],"hellinger"), method = 'bray')
mod <- betadisper(d = dis, group = factor(otu_all$plants), type = 'centroid')

#mod
#print(anova(mod));TukeyHSD(mod);TukeyHSD(mod)

p <- adonis2(dis~otu_all$plants)
print(p)

# (1) old betadispersion
plotcol <- c('red','orange',"#20B2AA",'blue',"#581845")

#pdf("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Bacteria/otu/Betadisper/Bacteria-Bray-Betadisper.pdf",height = 4,width=4)
mar=c(0.5, 0.5, 0.5, 0.5)

plot(mod, col=plotcol,hull = FALSE,cex = 1,label.cex = 0.6,
     main="",xlab="PC1", ylab="PC2",sub="Bray",seg.col=plotcol)
title(paste0("Bacteria-Betadispersion"),cex =0.8, font =2,line = 2)
mtext(side = 3, sprintf("Adonis: F = %.3f; P = %.3f", p$F[1],p$`Pr(>F)`[1]), 
      col="red", cex =0.6, font =2,line = 0.8)
mtext(side = 3, sprintf("Betadisper: F = %.3f; P = %.3f",anova(mod)$`F value`[1], anova(mod)$`Pr(>F)`[1]), 
      col="red", cex =0.6, font =2,line = 0)

#dev.off()

# (2) new betadispersion
df <- data.frame(mod$distances,mod$group)

ST <- kruskal(mod$distances,mod$group, p.adj = "fdr")

statis <- as.data.frame(rbind(ST$statistics[,1:2]))

rp.value <- data.frame(
  label=sprintf("P = %.3e (χ² = %.3g)", 
                statis$p.chisq,statis$Chisq),
  x = "Tamarix chinensis",
  y=0.55)

statis1 <- as.data.frame(rbind(ST$groups))
statis2 <- as.data.frame(rbind(ST$means))

p1 <- ggplot(df, aes(y=mod.distances, x = factor(mod.group))) +
  stat_boxplot(geom = "errorbar", width=0.3) +
  geom_boxplot(width = 0.5)
ymaxdata <- layer_data(p1) 
statis2$ymax <- ymaxdata$ymax

statis1$id <- rownames(statis1)
statis2$id <- rownames(statis2)
statis2 <- merge(statis2, statis1, by = "id")

multcomp.data <- data.frame(
  abc = factor(statis2$groups),
  x     = statis2$id,
  y     = as.numeric(statis2$ymax))

p2_bac <- ggplot(df, aes(y=mod.distances, x = factor(mod.group, levels = c("Bare land","Suaeda","Tamarix chinensis","Cotton","Maize")))) +
          stat_boxplot(geom = "errorbar", width=0.3) +
          geom_boxplot(width = 0.5) +
          #geom_jitter(size = 0.8) +
          labs(x = "Habitat", y= "Distance to centroid", title = "Bacteria-Betadispersion") +
          scale_x_discrete(labels = c(
            'Bare land' = "Bareland", 
            'Cotton' = "Cotton", 
            'Maize' = "Maize", 
            'Suaeda' = "Suaeda",
            'Tamarix chinensis' = "Tamarix")) +
          geom_text(
            data  = rp.value, mapping = aes(x = x, y = y, label = label),parse = F,  col="red", hjust = 0.5, size = 5) + 
          geom_text(data = multcomp.data, aes(x = x,y = y+0.02,label=abc),
                    color = "black",
                    size = 6, hjust = 0.5) +
          theme_bw() +
          ylim(0.20,0.6) +
          theme(panel.grid = element_blank(), 
                axis.ticks.y = element_line(color = "black",linewidth = 0.5)) +
          theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
                axis.title = element_text(size = 16, face = "bold"),
                axis.title.x = element_blank(),
                axis.text = element_text(size = 12, face = "bold",color = "black"))
p2_bac
#ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Bacteria/otu/Betadisper/Bacteria-Betadisper-Boxplot.pdf", p2_bac, height = 4,width=4.5)

# (3) boxplot of betadispersion
newplot("Bacteria-Betadispersion","E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Bacteria/otu/Betadisper/Bacteria-Betadispersion-PCoA-new.pdf")
p3_bac <- p3


### 3. Fungi-Bray
rm(list=setdiff(ls(), c("newplot", "p2_amf", "p3_amf", "p2_bac", "p3_bac")))
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Fungi/otu")

otu_all0 <- read.csv("otu_fungiFlattening.csv",check.names = F,row.names = 1,header = T)
otu_all0 <- as.data.frame(t(otu_all0))

group0 <- read.csv("sample_metadata.csv",header = T)
group0 <- na.omit(group0)
group <- group0[order(group0$sample.id),]
otu_all0$sample.id <- rownames(otu_all0)
identical(otu_all0$sample.id,group$sample.id)
otu_all <- merge(otu_all0,group,by= "sample.id")

dis <- vegdist(decostand(otu_all[,2:2512],"hellinger"), method = 'bray')
mod <- betadisper(d = dis, group = factor(otu_all$plants), type = 'centroid')

#mod
#print(anova(mod));TukeyHSD(mod);TukeyHSD(mod)

p <- adonis2(dis~otu_all$plants)
print(p)

# (1) old betadispersion
plotcol <- c('red','orange',"#20B2AA",'blue',"#581845")

#pdf("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Fungi/otu/Betadisper/Fungi-Bray-Betadisper.pdf",height = 4,width=4)
mar=c(0.5, 0.5, 0.5, 0.5)

plot(mod, col=plotcol,hull = FALSE,cex = 1,label.cex = 0.6,
     main="",xlab="PC1", ylab="PC2",sub="Bray",seg.col=plotcol)
title(paste0("Fungi-Betadispersion"),cex =0.8, font =2,line = 2)
mtext(side = 3, sprintf("Adonis: F = %.3f; P = %.3f", p$F[1],p$`Pr(>F)`[1]), 
      col="red", cex =0.6, font =2,line = 0.8)
mtext(side = 3, sprintf("Betadisper: F = %.3f; P = %.3f",anova(mod)$`F value`[1], anova(mod)$`Pr(>F)`[1]), 
      col="red", cex =0.6, font =2,line = 0)

#dev.off()

# (2) new betadispersion
df <- data.frame(mod$distances,mod$group)

ST <- kruskal(mod$distances,mod$group, p.adj = "fdr")

statis <- as.data.frame(rbind(ST$statistics[,1:2]))

rp.value <- data.frame(
  label=sprintf("P = %.3e (χ² = %.3g)", 
                statis$p.chisq,statis$Chisq),
  x = "Tamarix chinensis",
  y=0.65)

statis1 <- as.data.frame(rbind(ST$groups))
statis2 <- as.data.frame(rbind(ST$means))

p1 <- ggplot(df, aes(y=mod.distances, x = factor(mod.group))) +
  stat_boxplot(geom = "errorbar", width=0.3) +
  geom_boxplot(width = 0.5)
ymaxdata <- layer_data(p1) 
statis2$ymax <- ymaxdata$ymax

statis1$id <- rownames(statis1)
statis2$id <- rownames(statis2)
statis2 <- merge(statis2, statis1, by = "id")

multcomp.data <- data.frame(
  abc = factor(statis2$groups),
  x     = statis2$id,
  y     = as.numeric(statis2$ymax))

p2_fung <-  ggplot(df, aes(y=mod.distances, x = factor(mod.group, levels = c("Bare land","Suaeda","Tamarix chinensis","Cotton","Maize")))) +
            stat_boxplot(geom = "errorbar", width=0.3) +
            geom_boxplot(width = 0.5) +
            #geom_jitter(size = 0.8) +
            labs(x = "Habitat", y= "Distance to centroid", title = "Fungi-Betadispersion") +
            scale_x_discrete(labels = c(
                                        'Bare land' = "Bareland", 
                                        'Cotton' = "Cotton", 
                                        'Maize' = "Maize", 
                                        'Suaeda' = "Suaeda",
                                        'Tamarix chinensis' = "Tamarix")) +
            geom_text(
              data  = rp.value, mapping = aes(x = x, y = y, label = label),parse = F,  col="red", hjust = 0.5, size = 5) + 
            geom_text(data = multcomp.data, aes(x = x,y = y+0.03,label=abc),
                      color = "black",
                      size = 6, hjust = 0.5) +
            theme_bw() +
            ylim(0.25,0.7) +
            theme(panel.grid = element_blank(), 
                  axis.ticks.y = element_line(color = "black",linewidth = 0.5)) +
            theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
                  axis.title = element_text(size = 16, face = "bold"),
                  axis.title.x = element_blank(),
                  axis.text = element_text(size = 12, face = "bold",color = "black"))
p2_fung
#ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Fungi/otu/Betadisper/Fungi-Betadisper-Boxplot.pdf", p2_fung, height = 4,width=4.5)

# (3) boxplot of betadispersion
newplot("Fungi-Betadispersion","E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Fungi/otu/Betadisper/Fungi-Betadispersion-PCoA-new.pdf")
p3_fung <- p3


### 4. Protist-Bray
rm(list=setdiff(ls(), c("newplot", "p2_amf", "p3_amf", "p2_bac", "p3_bac", "p2_fung", "p3_fung")))
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Protist/otu")

otu_all0 <- read.csv("otu_protistFlattening.csv",check.names = F,row.names = 1,header = T)
otu_all0 <- as.data.frame(t(otu_all0))

group0 <- read.csv("sample_metadata.csv",header = T)
group0 <- na.omit(group0)
group <- group0[order(group0$sample.id),] 
otu_all0$sample.id <- rownames(otu_all0)
identical(otu_all0$sample.id,group$sample.id)
otu_all <- merge(otu_all0,group,by= "sample.id")

dis <- vegdist(decostand(otu_all[,2:2283],"hellinger"), method = 'bray')
mod <- betadisper(d = dis, group = factor(otu_all$plants), type = 'centroid')

#mod
#print(anova(mod));TukeyHSD(mod);TukeyHSD(mod)

p <- adonis2(dis~otu_all$plants)
print(p)

# (1) old betadispersion
plotcol <- c('red','orange',"#20B2AA",'blue',"#581845")

#pdf("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Protist/otu/Betadisper//Protist-Bray-Betadisper.pdf",height = 4,width=4)
mar=c(0.5, 0.5, 0.5, 0.5)

plot(mod, col=plotcol,hull = FALSE,cex = 1,label.cex = 0.6,
     main="",xlab="PC1", ylab="PC2",sub="Bray",seg.col=plotcol)
title(paste0("Protist-Betadispersion"),cex =0.8, font =2,line = 2)
mtext(side = 3, sprintf("Adonis: F = %.3f; P = %.3f", p$F[1],p$`Pr(>F)`[1]), 
      col="red", cex =0.6, font =2,line = 0.8)
mtext(side = 3, sprintf("Betadisper: F = %.3f; P = %.3f",anova(mod)$`F value`[1], anova(mod)$`Pr(>F)`[1]), 
      col="red", cex =0.6, font =2,line = 0)

#dev.off()

# (2) new betadispersion
df <- data.frame(mod$distances,mod$group)

ST <- kruskal(mod$distances,mod$group, p.adj = "fdr")

statis <- as.data.frame(rbind(ST$statistics[,1:2]))

rp.value <- data.frame(
  label=sprintf("P = %.3e (χ² = %.3g)", 
                statis$p.chisq,statis$Chisq),
  x = "Tamarix chinensis",
  y=0.47)

statis1 <- as.data.frame(rbind(ST$groups))
statis2 <- as.data.frame(rbind(ST$means))

p1 <- ggplot(df, aes(y=mod.distances, x = factor(mod.group))) +
  stat_boxplot(geom = "errorbar", width=0.3) +
  geom_boxplot(width = 0.5)
ymaxdata <- layer_data(p1) 
statis2$ymax <- ymaxdata$ymax

statis1$id <- rownames(statis1)
statis2$id <- rownames(statis2)
statis2 <- merge(statis2, statis1, by = "id")

multcomp.data <- data.frame(
  abc = factor(statis2$groups),
  x     = statis2$id,
  y     = as.numeric(statis2$ymax))

p2_prot <-  ggplot(df, aes(y=mod.distances, x = factor(mod.group, levels = c("Bare land","Suaeda","Tamarix chinensis","Cotton","Maize")))) +
            stat_boxplot(geom = "errorbar", width=0.3) +
            geom_boxplot(width = 0.5) +
            #geom_jitter(size = 0.8) +
            labs(x = "Habitat", y= "Distance to centroid", title = "Protist-Betadispersion") +
            scale_x_discrete(labels = c(
                                        'Bare land' = "Bareland", 
                                        'Cotton' = "Cotton", 
                                        'Maize' = "Maize", 
                                        'Suaeda' = "Suaeda",
                                        'Tamarix chinensis' = "Tamarix")) +
            geom_text(
              data  = rp.value, mapping = aes(x = x, y = y, label = label),parse = F,  col="red", hjust = 0.5, size = 5) + 
            geom_text(data = multcomp.data, aes(x = x,y = y+0.02,label=abc),
                      color = "black",
                      size = 6, hjust = 0.5) +
            theme_bw() +
            ylim(0.25,0.5) +
            theme(panel.grid = element_blank(), 
                  axis.ticks.y = element_line(color = "black",linewidth = 0.5)) +
            theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
                  axis.title = element_text(size = 16, face = "bold"),
                  axis.title.x = element_blank(),
                  axis.text = element_text(size = 12, face = "bold",color = "black"))
p2_prot
#ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Protist/otu/Betadisper/Protist-Betadisper-Boxplot.pdf", p2_prot, height = 4,width=4.5)

# (3) boxplot of betadispersion
newplot("Protists-Betadispersion","E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Protist/otu/Betadisper/Protist-Betadispersion-PCoA-new.pdf")
p3_prot <- p3

```{r,fig.align='center', fig.height=9, fig.width=20}

p_all <- (p3_amf + p3_bac + p3_fung + p3_prot + p2_amf + p2_bac + p2_fung + p2_prot) + 
      plot_layout(nrow = 2, ncol = 4, guides = "collect") #+
      # plot_annotation(tag_levels = 'a') &
      # theme(plot.tag = element_text(size = 20, face = "bold"),
      #       legend.justification = c(1, 0.85))

p_all

# saveRDS(p2_amf,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_boxplot_amf.rda")
# saveRDS(p2_bac,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_boxplot_bac.rda")
# saveRDS(p2_fung,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_boxplot_fung.rda")
# saveRDS(p2_prot,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_boxplot_prot.rda")
# saveRDS(p3_amf,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_amf.rda")
# saveRDS(p3_bac,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_bac.rda")
# saveRDS(p3_fung,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_fung.rda")
# saveRDS(p3_prot,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_prot.rda")
# 
# 
# ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/Betadisper.svg", p_all, height = 9,width=20)
# ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/Betadisper.pdf", p_all, height = 9,width=20)

```
