---
title: "Fig.4_Co-occurrance_network"
author: "Huanhuan Zhu"
date: "2025-02-17"
output: html_document
---

```{r, fig.align='center',fig.height = 8, fig.width=8, warning=FALSE, message=FALSE}

#############################Fig.4_Co-occurrance_network##########################

library(vegan)
library(psych)  # corr.test()for r and P of paired OTUs
library(igraph)
library(ggplot2)
library(colorRamps)
library(ape)
library(stringr)
library(reshape2)
library(splitstackshape)
library(emmeans)
library(graphics)
library(phyloseq)
library(dplyr)
library(ggraph)
library(pals)
library(RColorBrewer)
library(patchwork)
library(scales)  # pencentage of Y axis


### 1. AMF

rm(list=ls())
amf.network<-function(k,para){  # k for selecting MC(maize & cotton) or TS (Tamarix & Suaeda)
  
  setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/AMF/otu/")
  
  # Reading OTU table & metadata file
  otu_all <-read.csv("otu_amfFlattening.csv", row.names = 1, check.names = F, header = T)
  group <- read.csv("sample_metadata.csv", header = T)
  #group <- na.omit(group)
  
  group_MC <- group %>%
    filter(country == "Uzbekistan",plants=="Maize"|plants=="Cotton")
  group_MC$type <- rep("MC",nrow(group_MC))
  
  group_TS <- group %>%
    filter(country == "Uzbekistan",plants=="Tamarix chinensis"|plants=="Suaeda")
  group_TS$type <- rep("TS",nrow(group_TS))
  
  group2 <- rbind(group_MC,group_TS)
  
  env0 <- group2[order(group2$sample.id), ]
  
  ID0 <-read.csv("HMME.amf.OTU.ID1.csv", check.names = F, row.names = 1, header = T)
  names(ID0)[21] <- "Genus"
  ID0$Genus <- substr(ID0$Genus, 4, nchar(ID0$Genus))
  
  # Set node color
  color <- c(
    "Acaulospora" = "#ff00ff"
    , "Ambispora" = "#00ff00"
    , "Archaeospora" = "deepskyblue"
    , "Claroideoglomus" = "gold"
    , "Diversispora" = "red"
    , "Geosiphon " = "navy"
    , "Gigaspora" = "darkgreen"
    , "Glomus" = "maroon3"
    , "Kuklospora" = "black"
    , "Paraglomus" = "bisque"
    , "Scutellospora" = "blue")
  
  test <- as.data.frame(rowSums(otu_all))
  test$id <- rownames(test)
  test2 <- test[order(test$`rowSums(otu_all)`,decreasing = T),]
  otu_all <- otu_all[test2[test2$`rowSums(otu_all)`>= sum(test2$`rowSums(otu_all)`)*0.000,]$id,]
  
  #Subset data
  env.tmp<-env0[env0$type==k,]
  
  otu_all2 <- otu_all[,colnames(otu_all) %in% env.tmp$sample.id]
  ID.tmp0<-ID0[ID0$OTU.ID %in% colnames(otu_all),]
  
  # Remove OTUs that are less than 5 sequences in all samples and at least exist in 2 samples(20%)
  otu <- t(otu_all2)[,specnumber(otu_all2) >= ncol(otu_all2)*para & colSums(t(otu_all2)) > 4]
  
  otu2 <- otu_all2[colnames(otu),]
  otu2$otusum <- rowSums(otu2)  
  otu2$abu <- otu2$otusum/sum(otu2$otusum)
  
  # Spearman's Rho calculation
  spman.r0 = corr.test(otu, use="pairwise",method="spearman",adjust="fdr", alpha = .05, ci=FALSE)
  
  # Matrix to dataframe
  Cor<-as.matrix(spman.r0$r)  
  Cor[lower.tri(Cor)] <- NA  # Keep upper triangle
  diag(Cor) <- NA  # Remove diagnoal
  Cor.df <- reshape2::melt(Cor, na.rm = TRUE)  # Long format
  
  P0<-as.matrix(spman.r0$p)
  P0[lower.tri(P0)] <- NA
  diag(P0) <- NA
  P.df <- reshape2::melt(P0, na.rm = TRUE) 
  
  df <- merge(Cor.df, P.df, by=c("Var1","Var2"))
  names(df) <- c("row","col","Cor","p")
  
  # Spearman's rho > 0.6 & p-value < 0.05 to select edges in network
  da.tmp <- df.sig <- filter(df, abs(Cor) >= 0.6, p < 0.05)
  
  da.g1 <- data.frame(da.tmp)
  #da.g1 <- na.omit(da.g1)
  
  # Construct igraph g for plotting co-occurence network
  g <- graph_from_data_frame(da.g1, directed=FALSE, vertices = NULL)
  
  fc <- cluster_fast_greedy(g)  # Cluster by fast greedy for modularity
  print(modularity(fc))  # >0.4 indicate modular structures
  modularity(fc,membership(fc))
  print(sizes(fc))
  
  # Whole network properties
  net.metrics <- matrix(nrow=22,ncol=1)
  net.metrics[1,1] <- length(E(g))  # length(curve_multiple(funteria.fungi.archea.g))
  net.metrics[2,1] <- length(V(g))
  #net.fun.metrics[3,1] <- connectedness(as.matrix(as_adjacency_matrix(igraph, type = c("both"))))  # connectedness FROM sna package; This package will affect other network properties
  net.metrics[4,1] <- edge_density(g,loops=FALSE)
  net.metrics[5,1] <- mean(igraph::degree(g))
  net.metrics[6,1] <- average.path.length(g) 
  net.metrics[7,1] <- diameter(g, directed = FALSE, unconnected = TRUE, weights = NA)
  net.metrics[8,1] <- edge_connectivity(g)
  net.metrics[9,1] <- vertex_connectivity(g)
  net.metrics[10,1] <- cohesion(g)
  net.metrics[11,1] <- transitivity(g)
  net.metrics[12,1] <- no.clusters(g)
  net.metrics[13,1] <- sum(graph.knn(g)$knn[!is.na(graph.knn(g)$knn)])/length(V(g))
  net.metrics[14,1] <- centralization.closeness(g)$centralization
  net.metrics[15,1] <- centralization.betweenness(g)$centralization
  net.metrics[16,1] <- centralization.degree(g)$centralization
  net.metrics[17,1] <- assortativity.degree(g)
  fc <- cluster_fast_greedy(g)
  net.metrics[18,1] <- modularity(g,membership(fc))
  net.metrics[19,1] <- mean(igraph::betweenness(g))
  net.metrics[20,1] <- diameter(g, directed = FALSE, unconnected = TRUE)
  net.metrics[21,1] <- sum(E(g)$Cor>0)  # number of positive correlation
  net.metrics[22,1] <- sum(E(g)$Cor<0)  # number of negative correlation
  
  rownames(net.metrics) <- c("num.edges","num.vertices","connectedness","connectance","average.degree","average.path.length","diameter",
                             "edge_connectivity","vertex.connectivity","cohesion","clustering.coefficient","no.clusters","avenei","centralization.closeness",
                             "centralization.betweenness","centralization.degree","assortativity.degree","modularity","average.betweenness","w.diameter","no.positive","no.negative")
  colnames(net.metrics) <- k
  print(net.metrics)
  
  net.metrics <- as.data.frame(net.metrics)
  #net.metrics$name <- rownames(net.metrics)
  net.metrics1 <<- net.metrics
  
  # Parameters for plot, parameters for E(g) is parameters for da.g1, reset parameters for V(g)
  # set vertices size
  v.size <- otu2[V(g)$name, ]  # V(g)$name, name of all vertices
  v.size1 = log(v.size$abu * 100000)  # origin value*100, then e-logarithm (to show logarithmic differences in the data)
  V(g)$size =  abs(v.size1)
  
  # set edge color, postive correlation to red, negative correlation to blue
  E.color <-  E(g)$Cor
  E.color = ifelse(E.color > 0, "red",ifelse(E.color < 0, "blue", "grey"))
  E(g)$color = as.character(E.color) 
  
  # color by Vertices/node with genus
  V(g)$genus <- ID0$Genus[match(V(g)$name, ID0$OTU.ID)]  # match find which rows of ID match to names of V(g); first element in second element
  #V(g)$color <- ID0$color[match(V(g)$name, ID0$OTU.ID)]
  
  # Set edge width
  E(g)$width = abs(E(g)$Cor)
  
  # Set title
  # title=paste("AMF",k,sep="-")
  name <- c("MC" = "Farmland", "TS" = "Wildland")
  
  # Plot with ggraph
  set.seed(123)
  p1 <<-  ggraph(g, layout = "nicely") + 
    geom_edge_bend(aes(width = abs(E(g)$Cor), color = E(g)$color), strength = 0.2) +  # strength for curvature
    scale_edge_colour_manual(values= c("blue"="blue", "red"="red")) +
    scale_edge_width_continuous(range = c(0.5, 1.2)) +  # Sets the thickness range of the edge
    geom_node_point(aes(color = factor(V(g)$genus), size = V(g)$size)) +
    scale_colour_manual(name = "Genus",values = color) +
    scale_size_continuous(range = c(1,5)) +
    #geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    labs(title=sprintf("AM fungi-%s",name[k]),
         subtitle =  sprintf("Vertice = %d; Edge = %d", 
                             net.metrics["num.vertices", ], 
                             net.metrics["num.edges", ])) +
    guides(edge_colour = "none", edge_width = "none", size = "none") +
    theme_void() +
    theme(
      plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"), 
      plot.title = element_text(size = 20, face = "bold",hjust=0.5, margin = margin(b = 10)),
      plot.subtitle = element_text(size = 12, face = "bold",hjust=0.5, color="red", margin = margin(b = 10)), 
      legend.title = element_text(colour = "black", size = 15,face = "bold"),
      legend.text = element_text(colour = "black", size = 12,face = "bold"))  
  p1
}


amf.network("MC", 0.2)
net.metrics <- net.metrics1
p_amf_mc <- p1
amf.network("TS", 0.2)
net.metrics$TS <- net.metrics1$TS
p_amf_ts <- p1

property <- function(title){
  net.metrics <- net.metrics[c("num.edges", 
                               "num.vertices", 
                               "average.degree", 
                               "average.path.length", 
                               "diameter", 
                               "connectance", 
                               "clustering.coefficient", 
                               "modularity"),]
  net.metrics$para <- rownames(net.metrics)
  net.metrics1 <- melt(net.metrics,id="para")
  net.metrics1[is.nan(net.metrics1$value),]$value <- 0
  net.metrics1$group <- title
  net.metrics_tmp <<- net.metrics1
}


property("AM fungi")  # 6,3.5
net.metrics_amf <- net.metrics_tmp


### 2. Bacteria

rm(list=setdiff(ls(), c("property",
                        "p_amf_mc", "p_amf_ts", "net.metrics_amf")))

bacteria.network<-function(k,para){
  
  setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Bacteria/otu/")
  
  otu_all <-read.csv("otu_bacteriaFlattening.csv", row.names = 1, check.names = F, header = T)
  group <- read.csv("sample_metadata.csv", header = T)
  #group <- na.omit(group)
  
  group_MC <- group %>%
    filter(country == "Uzbekistan",plants=="Maize"|plants=="Cotton")
  group_MC$type <- rep("MC",nrow(group_MC))
  
  group_TS <- group %>%
    filter(country == "Uzbekistan",plants=="Tamarix chinensis"|plants=="Suaeda")
  group_TS$type <- rep("TS",nrow(group_TS))
  
  group2 <- rbind(group_MC,group_TS)
  
  env0 <- group2[order(group2$sample.id), ]
  
  ID0 <-read.csv("HMME.bact.OTU.ID1.csv", check.names = F, row.names = 1, header = T)
  names(ID0)[12] <- "Phylum"
  
  # Set node color
  color <- c(
    "Proteobacteria" = "#ff00ff"
    , "Actinobacteriota" = "#00ff00"
    , "Firmicutes" = "deepskyblue"
    , "Planctomycetota" = "gold"
    , "Chloroflexi" = "red"
    , "Verrucomicrobiota" = "navy"
    , "Crenarchaeota" = "darkgreen"
    , "Gemmatimonadota" = "maroon3"
    , "Nitrospirota" = "black"
    , "Acidobacteriota" = "blue"
    , "Methylomirabilota" = "purple"
    , "Armatimonadota" = "chocolate"
    , "Latescibacterota" = "turquoise"
    , "myxococcota" = "darkred"
    , "Thermoplasmatota" = "tan")
  
  test <- as.data.frame(rowSums(otu_all))
  test$id <- rownames(test)
  test2 <- test[order(test$`rowSums(otu_all)`,decreasing = T),]
  otu_all <- otu_all[test2[test2$`rowSums(otu_all)` >= sum(test2$`rowSums(otu_all)`)*0.000,]$id,]
  
  # Subset data
  env.tmp<-env0[env0$type==k,]
  
  otu_all2 <- otu_all[,colnames(otu_all) %in% env.tmp$sample.id] 
  ID.tmp0<-ID0[ID0$OTU.ID %in% colnames(otu_all),]
  
  otu <- t(otu_all2)[,specnumber(otu_all2) >= ncol(otu_all2)*para & colSums(t(otu_all2)) > 4]
  
  otu2 <- otu_all2[colnames(otu),]
  otu2$otusum <- rowSums(otu2)  
  otu2$abu <- otu2$otusum/sum(otu2$otusum)
  
  spman.r0 = corr.test(otu, use="pairwise",method="spearman",adjust="fdr", alpha = .05, ci=FALSE)
  
  Cor<-as.matrix(spman.r0$r)  
  Cor[lower.tri(Cor)] <- NA 
  diag(Cor) <- NA 
  Cor.df <- reshape2::melt(Cor, na.rm = TRUE)
  
  P0<-as.matrix(spman.r0$p)
  P0[lower.tri(P0)] <- NA
  diag(P0) <- NA
  P.df <- reshape2::melt(P0, na.rm = TRUE)
  
  df <- merge(Cor.df, P.df, by=c("Var1","Var2"))
  names(df) <- c("row","col","Cor","p")
  
  da.tmp <- df.sig <- filter(df, abs(Cor) >= 0.6, p < 0.05)
  
  da.g1 <- data.frame(da.tmp)
  #da.g1 <- na.omit(da.g1)
  
  g <- graph_from_data_frame(da.g1, 
                             directed=FALSE,
                             vertices = NULL)
  
  fc <- cluster_fast_greedy(g)
  print(modularity(fc))  # >0.4 indicate modular structures
  modularity(fc,membership(fc))
  print(sizes(fc))
  
  # whole network properties
  net.metrics <- matrix(nrow=22,ncol=1)
  net.metrics[1,1] <- length(E(g)) #length(curve_multiple(funteria.fungi.archea.g))
  net.metrics[2,1] <- length(V(g))
  #net.fun.metrics[3,1] <- connectedness(as.matrix(as_adjacency_matrix(igraph, type = c("both"))))
  net.metrics[4,1] <- edge_density(g,loops=FALSE)
  net.metrics[5,1] <- mean(igraph::degree(g))
  net.metrics[6,1] <- average.path.length(g) 
  net.metrics[7,1] <- diameter(g, directed = FALSE, unconnected = TRUE, weights = NA)
  net.metrics[8,1] <- edge_connectivity(g)
  net.metrics[9,1] <- vertex_connectivity(g)
  net.metrics[10,1] <- cohesion(g)
  net.metrics[11,1] <- transitivity(g)
  net.metrics[12,1] <- no.clusters(g)
  net.metrics[13,1] <- sum(graph.knn(g)$knn[!is.na(graph.knn(g)$knn)])/length(V(g))
  net.metrics[14,1] <- centralization.closeness(g)$centralization
  net.metrics[15,1] <- centralization.betweenness(g)$centralization
  net.metrics[16,1] <- centralization.degree(g)$centralization
  net.metrics[17,1] <- assortativity.degree(g)
  fc <- cluster_fast_greedy(g)
  net.metrics[18,1] <- modularity(g,membership(fc))
  net.metrics[19,1] <- mean(igraph::betweenness(g))
  net.metrics[20,1] <- diameter(g, directed = FALSE, unconnected = TRUE)
  net.metrics[21,1] <- sum(E(g)$Cor>0)  # number of positive correlation
  net.metrics[22,1] <- sum(E(g)$Cor<0)  # number of negative correlation
  
  rownames(net.metrics) <- c("num.edges","num.vertices","connectedness","connectance","average.degree","average.path.length","diameter",
                             "edge_connectivity","vertex.connectivity","cohesion","clustering.coefficient","no.clusters","avenei","centralization.closeness",
                             "centralization.betweenness","centralization.degree","assortativity.degree","modularity","average.betweenness","w.diameter","no.positive","no.negative")
  colnames(net.metrics) <- k
  #write.csv(net.bac.metrics,"16S.AU50.all.net.metricsHEL.csv")
  print(net.metrics)
  
  net.metrics <- as.data.frame(net.metrics)
  #net.metrics$name <- rownames(net.metrics)
  net.metrics1 <<- net.metrics
  
  # set vertices size
  v.size <- otu2[V(g)$name, ] 
  v.size1 = log(v.size$abu * 100000)
  V(g)$size =  abs(v.size1)
  
  E.color <-  E(g)$Cor
  E.color = ifelse(E.color > 0, "red",ifelse(E.color < 0, "blue", "grey"))
  E(g)$color = as.character(E.color) 
  
  # color by Vertices/node with Phylum
  V(g)$Phylum <- ID0$Phylum[match(V(g)$name, ID0$OTU.ID)]
  #V(g)$color <- ID0$color[match(V(g)$name, ID0$OTU.ID)]
  
  E(g)$width = abs(E(g)$Cor)
  
  # title=paste("AMF",k,sep="-")
  name <- c("MC" = "Farmland", "TS" = "Wildland")
  
  set.seed(123)
  p1 <<-  ggraph(g, layout = "nicely") + 
    geom_edge_bend(aes(width = abs(E(g)$Cor), color = E(g)$color), strength = 0.2) +
    scale_edge_colour_manual(values= c("blue"="blue", "red"="red")) +
    scale_edge_width_continuous(range = c(0.5, 1.2)) + 
    geom_node_point(aes(color=factor(V(g)$Phylum), size = V(g)$size)) +
    scale_colour_manual(name="Phylum",values=color) +
    scale_size_continuous(range = c(1,5)) +
    #geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    labs(title=sprintf("Prokaryotes-%s",name[k]),
         subtitle =  sprintf("Vertice = %d; Edge = %d", 
                             net.metrics["num.vertices", ], 
                             net.metrics["num.edges", ])) +
    guides(edge_colour="none", edge_width="none", size = "none") +
    theme_void() +
    theme(
      plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"), 
      plot.title = element_text(size = 20, face = "bold",hjust=0.5, margin = margin(b = 10)),
      plot.subtitle = element_text(size = 12, face = "bold",hjust=0.5, color="red", margin = margin(b = 10)), 
      legend.title = element_text(colour = "black", size = 15,face = "bold"),
      legend.text = element_text(colour = "black", size = 12,face = "bold"))
  p1
}

bacteria.network("MC",0.2)
net.metrics <- net.metrics1
p_bac_mc <- p1
bacteria.network("TS",0.2)
net.metrics$TS <- net.metrics1$TS
p_bac_ts <- p1


property <- function(title){
  net.metrics <- net.metrics[c("num.edges", 
                               "num.vertices", 
                               "average.degree", 
                               "average.path.length", 
                               "diameter", 
                               "connectance", 
                               "clustering.coefficient", 
                               "modularity"),]
  net.metrics$para <- rownames(net.metrics)
  net.metrics1 <- melt(net.metrics,id="para")
  #net.metrics1[is.nan(net.metrics1$value),]$value <- 0
  net.metrics1$group <- title
  net.metrics_tmp <<- net.metrics1
}

property("Prokaryotes")
net.metrics_prok <- rbind(net.metrics_tmp,net.metrics_amf)



### 3. Fungal

rm(list=setdiff(ls(), c("property",
                        "p_amf_mc", "p_amf_ts", 
                        "p_bac_mc", "p_bac_ts", "net.metrics_prok")))

fungi.network<-function(k,para){
  
  setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Fungi/otu/")
  
  otu_all <-read.csv("otu_fungiFlattening.csv", row.names = 1, check.names = F, header = T)
  group <- read.csv("sample_metadata.csv", header = T)
  #group <- na.omit(group)
  
  group_MC <- group %>%
    filter(country == "Uzbekistan",plants=="Maize"|plants=="Cotton")
  group_MC$type <- rep("MC",nrow(group_MC))
  
  group_TS <- group %>%
    filter(country == "Uzbekistan",plants=="Tamarix chinensis"|plants=="Suaeda")
  group_TS$type <- rep("TS",nrow(group_TS))
  
  group2 <- rbind(group_MC,group_TS)
  
  env0 <- group2[order(group2$sample.id), ]
  
  ID0 <-read.csv("HMME.fung.OTU.ID1.csv", check.names = F, row.names = 1, header = T)
  names(ID0)[12] <- "Phylum"
  ID0$Phylum <- substr(ID0$Phylum, 4, nchar(ID0$Phylum))
  
  # Set node color
  color <- c(
    "Ascomycota" = "#ff00ff"
    , "Basidiomycota" = "#00ff00"
    , "Mortierellomycota" = "deepskyblue"
    , "Glomeromycota" = "gold"
    , "Chytridiomycota" = "red"
    , "Mucoromycota" = "navy"
    , "Kickxellomycota" = "darkgreen"
    , "Fungi_phy_Incertae_sedis" = "maroon3"
    , "Monoblepharomycota" = "black"
    , "Rozellomycota" = "turquoise"
    , "Aphelidiomycota" = "tan"
    , "Zoopagomycota" = "blue"
    , "_" = "purple")
  
  test <- as.data.frame(rowSums(otu_all))
  test$id <- rownames(test)
  test2 <- test[order(test$`rowSums(otu_all)`,decreasing = T),]
  otu_all <- otu_all[test2[test2$`rowSums(otu_all)` >= sum(test2$`rowSums(otu_all)`)*0.000,]$id,]
  
  # Subset data
  env.tmp<-env0[env0$type==k,]
  
  otu_all2 <- otu_all[,colnames(otu_all) %in% env.tmp$sample.id]
  ID.tmp0<-ID0[ID0$OTU.ID %in% colnames(otu_all),]
  
  otu <- t(otu_all2)[,specnumber(otu_all2) >= ncol(otu_all2)*para & colSums(t(otu_all2)) > 4]
  
  otu2 <- otu_all2[colnames(otu),]
  otu2$otusum <- rowSums(otu2)  
  otu2$abu <- otu2$otusum/sum(otu2$otusum)
  
  spman.r0 = corr.test(otu, use="pairwise",method="spearman",adjust="fdr", alpha = .05, ci=FALSE)
  
  Cor<-as.matrix(spman.r0$r)  
  Cor[lower.tri(Cor)] <- NA
  diag(Cor) <- NA
  Cor.df <- reshape2::melt(Cor, na.rm = TRUE) 
  
  P0<-as.matrix(spman.r0$p)
  P0[lower.tri(P0)] <- NA
  diag(P0) <- NA
  P.df <- reshape2::melt(P0, na.rm = TRUE)
  
  df <- merge(Cor.df, P.df, by=c("Var1","Var2"))
  names(df) <- c("row","col","Cor","p")
  
  da.tmp <- df.sig <- filter(df, abs(Cor) >= 0.6, p < 0.05)
  
  da.g1 <- data.frame(da.tmp)
  #da.g1 <- na.omit(da.g1)
  
  g <- graph_from_data_frame(da.g1, 
                             directed=FALSE,
                             vertices = NULL)
  
  fc <- cluster_fast_greedy(g) 
  print(modularity(fc))  # >0.4 indicate modular structures
  modularity(fc,membership(fc))
  print(sizes(fc))
  
  # whole network properties
  net.metrics <- matrix(nrow=22,ncol=1)
  net.metrics[1,1] <- length(E(g))##length(curve_multiple(funteria.fungi.archea.g))
  net.metrics[2,1] <- length(V(g))
  #net.fun.metrics[3,1] <- connectedness(as.matrix(as_adjacency_matrix(igraph, type = c("both"))))
  net.metrics[4,1] <- edge_density(g,loops=FALSE)
  net.metrics[5,1] <- mean(igraph::degree(g))
  net.metrics[6,1] <- average.path.length(g) 
  net.metrics[7,1] <- diameter(g, directed = FALSE, unconnected = TRUE, weights = NA)
  net.metrics[8,1] <- edge_connectivity(g)
  net.metrics[9,1] <- vertex_connectivity(g)
  net.metrics[10,1] <- cohesion(g)
  net.metrics[11,1] <- transitivity(g)
  net.metrics[12,1] <- no.clusters(g)
  net.metrics[13,1] <- sum(graph.knn(g)$knn[!is.na(graph.knn(g)$knn)])/length(V(g))
  net.metrics[14,1] <- centralization.closeness(g)$centralization
  net.metrics[15,1] <- centralization.betweenness(g)$centralization
  net.metrics[16,1] <- centralization.degree(g)$centralization
  net.metrics[17,1] <- assortativity.degree(g)
  fc <- cluster_fast_greedy(g)
  net.metrics[18,1] <- modularity(g,membership(fc))
  net.metrics[19,1] <- mean(igraph::betweenness(g))
  net.metrics[20,1] <- diameter(g, directed = FALSE, unconnected = TRUE)
  net.metrics[21,1] <- sum(E(g)$Cor>0)  # number of positive correlation
  net.metrics[22,1] <- sum(E(g)$Cor<0)  # number of negative correlation
  
  rownames(net.metrics) <- c("num.edges","num.vertices","connectedness","connectance","average.degree","average.path.length","diameter",
                             "edge_connectivity","vertex.connectivity","cohesion","clustering.coefficient","no.clusters","avenei","centralization.closeness",
                             "centralization.betweenness","centralization.degree","assortativity.degree","modularity","average.betweenness","w.diameter","no.positive","no.negative")
  colnames(net.metrics) <- k
  #write.csv(net.bac.metrics,"16S.AU50.all.net.metricsHEL.csv")
  print(net.metrics)
  
  net.metrics <- as.data.frame(net.metrics)
  #net.metrics$name <- rownames(net.metrics)
  net.metrics1 <<- net.metrics
  
  # set vertices size
  v.size <- otu2[V(g)$name, ] 
  v.size1 = log(v.size$abu * 100000) 
  V(g)$size =  abs(v.size1)
  
  E.color <-  E(g)$Cor
  E.color = ifelse(E.color > 0, "red",ifelse(E.color < 0, "blue", "grey"))
  E(g)$color = as.character(E.color) 
  
  # color by Vertices/node with Phylum
  V(g)$Phylum <- ID0$Phylum[match(V(g)$name, ID0$OTU.ID)]
  #V(g)$color <- ID0$color[match(V(g)$name, ID0$OTU.ID)]
  
  E(g)$width = abs(E(g)$Cor)
  
  # title=paste("AMF",k,sep="-")
  name <- c("MC" = "Farmland", "TS" = "Wildland")
  
  set.seed(123)
  p1 <<-  ggraph(g, layout = "nicely") + 
    geom_edge_bend(aes(width = abs(E(g)$Cor), color = E(g)$color), strength = 0.2) + 
    scale_edge_colour_manual(values= c("blue"="blue", "red"="red")) +
    scale_edge_width_continuous(range = c(0.5, 1.2)) +
    geom_node_point(aes(color=factor(V(g)$Phylum), size = V(g)$size)) +
    scale_colour_manual(name="Phylum",values=color) +
    scale_size_continuous(range = c(1,5)) +
    #geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    labs(title=sprintf("Fungi-%s",name[k]),
         subtitle =  sprintf("Vertice = %d; Edge = %d", 
                             net.metrics["num.vertices", ], 
                             net.metrics["num.edges", ])) +
    guides(edge_colour="none", edge_width="none", size = "none") +
    theme_void() +
    theme(
      plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"), 
      plot.title = element_text(size = 20, face = "bold",hjust=0.5, margin = margin(b = 10)),
      plot.subtitle = element_text(size = 12, face = "bold",hjust=0.5, color="red", margin = margin(b = 10)), 
      legend.title = element_text(colour = "black", size = 15,face = "bold"),
      legend.text = element_text(colour = "black", size = 12,face = "bold"))
  p1
}

fungi.network("MC",0.2)
net.metrics <- net.metrics1
p_fung_mc <- p1
fungi.network("TS",0.2)
net.metrics$TS <- net.metrics1$TS
p_fung_ts <- p1


property("Fungi")
net.metrics_fung <- rbind(net.metrics_prok,net.metrics_tmp)



### 4. Protist

rm(list=setdiff(ls(), c("property",
                        "p_amf_mc", "p_amf_ts",
                        "p_bac_mc", "p_bac_ts", 
                        "p_fung_mc", "p_fung_ts", "net.metrics_fung")))

protist.network<-function(k,para){
  
  setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Protist/otu/")
  
  otu_all <-read.csv("otu_protistFlattening.csv", row.names = 1, check.names = F, header = T)
  group <- read.csv("sample_metadata.csv", header = T)
  #group <- na.omit(group)
  
  group_MC <- group %>%
    filter(country == "Uzbekistan",plants=="Maize"|plants=="Cotton")
  group_MC$type <- rep("MC",nrow(group_MC))
  
  group_TS <- group %>%
    filter(country == "Uzbekistan",plants=="Tamarix chinensis"|plants=="Suaeda")
  group_TS$type <- rep("TS",nrow(group_TS))
  
  group2 <- rbind(group_MC,group_TS)
  
  env0 <- group2[order(group2$sample.id), ]
  
  ID0 <-read.csv("HMME.prot.OTU.ID1.csv", check.names = F, row.names = 1, header = T)
  names(ID0)[13] <- "Phylum"
  ID0$Phylum <- substr(ID0$Phylum, 3, nchar(ID0$Phylum))
  
  # Set node color
  color <- c(
    "Alveolata-Ciliophora" = "#ff00ff"
    , "Alveolata-Apicomplexa" = "chocolate"
    , "Centroplasthelida-Centroplasthelida_X" = "turquoise"
    , "Chlorophyta-Chlorophyta_X" = "#00ff00"
    , "Cryptophyta-Cryptophyta_X" = "darkred"
    , "Evosea-Evosea_X" = "deepskyblue"
    , "Glaucophyta-Glaucophyta_X" = "salmon"
    , "Opisthokonta-Choanoflagellata" = "tan"
    , "Opisthokonta-Opisthokonta X" = "purple"
    , "Picozoa-Picozoa_X" = "peru"
    , "Streptophyta-Streptophyta_X" = "blue"
    , "Rhizaria-Cercozoa" = "gold"
    , "Stramenopiles-Bigyra" = "red"
    , "Tubulinea-Tubulinea_X" = "navy"
    , "Stramenopiles-Gyrista" = "darkgreen"
    , "Discoba-Discoba_X" = "maroon3"
    , "Ancyromonadida-Ancyromonadida_X" = "black"
    , "Rhodelphidia-Rhodelphidia_X" = "bisque")
  
  test <- as.data.frame(rowSums(otu_all))
  test$id <- rownames(test)
  test2 <- test[order(test$`rowSums(otu_all)`,decreasing = T),]
  otu_all <- otu_all[test2[test2$`rowSums(otu_all)` >= sum(test2$`rowSums(otu_all)`)*0.000,]$id,]
  
  
  #Subset data
  env.tmp<-env0[env0$type==k,]
  
  otu_all2 <- otu_all[,colnames(otu_all) %in% env.tmp$sample.id]  
  ID.tmp0<-ID0[ID0$OTU.ID %in% colnames(otu_all),] 
  
  otu <- t(otu_all2)[,specnumber(otu_all2) >= ncol(otu_all2)*para & colSums(t(otu_all2)) > 4]
  
  otu2 <- otu_all2[colnames(otu),]
  otu2$otusum <- rowSums(otu2)  
  otu2$abu <- otu2$otusum/sum(otu2$otusum)
  
  spman.r0 = corr.test(otu, use="pairwise",method="spearman",adjust="fdr", alpha = .05, ci=FALSE)
  
  Cor<-as.matrix(spman.r0$r)  
  Cor[lower.tri(Cor)] <- NA 
  diag(Cor) <- NA 
  Cor.df <- reshape2::melt(Cor, na.rm = TRUE) 
  
  P0<-as.matrix(spman.r0$p)
  P0[lower.tri(P0)] <- NA 
  diag(P0) <- NA 
  P.df <- reshape2::melt(P0, na.rm = TRUE) 
  
  df <- merge(Cor.df, P.df, by=c("Var1","Var2"))
  names(df) <- c("row","col","Cor","p")
  
  da.tmp <- df.sig <- filter(df, abs(Cor) >= 0.6, p < 0.05)
  
  da.g1 <- data.frame(da.tmp)
  #da.g1 <- na.omit(da.g1)
  
  g <- graph_from_data_frame(da.g1, 
                             directed=FALSE,  
                             vertices = NULL) 
  
  fc <- cluster_fast_greedy(g) 
  print(modularity(fc))  # >0.4 indicate modular structures
  modularity(fc,membership(fc))
  print(sizes(fc))
  
  # whole network properties
  net.metrics <- matrix(nrow=22,ncol=1)
  net.metrics[1,1] <- length(E(g))##length(curve_multiple(funteria.fungi.archea.g))
  net.metrics[2,1] <- length(V(g))
  #net.fun.metrics[3,1] <- connectedness(as.matrix(as_adjacency_matrix(igraph, type = c("both"))))
  net.metrics[4,1] <- edge_density(g,loops=FALSE)
  net.metrics[5,1] <- mean(igraph::degree(g))
  net.metrics[6,1] <- average.path.length(g) 
  net.metrics[7,1] <- diameter(g, directed = FALSE, unconnected = TRUE, weights = NA)
  net.metrics[8,1] <- edge_connectivity(g)
  net.metrics[9,1] <- vertex_connectivity(g)
  net.metrics[10,1] <- cohesion(g)
  net.metrics[11,1] <- transitivity(g)
  net.metrics[12,1] <- no.clusters(g)
  net.metrics[13,1] <- sum(graph.knn(g)$knn[!is.na(graph.knn(g)$knn)])/length(V(g))
  net.metrics[14,1] <- centralization.closeness(g)$centralization
  net.metrics[15,1] <- centralization.betweenness(g)$centralization
  net.metrics[16,1] <- centralization.degree(g)$centralization
  net.metrics[17,1] <- assortativity.degree(g)
  fc <- cluster_fast_greedy(g)
  net.metrics[18,1] <- modularity(g,membership(fc))
  net.metrics[19,1] <- mean(igraph::betweenness(g))
  net.metrics[20,1] <- diameter(g, directed = FALSE, unconnected = TRUE)
  net.metrics[21,1] <- sum(E(g)$Cor>0)  # number of positive correlation
  net.metrics[22,1] <- sum(E(g)$Cor<0)  # number of negative correlation
  
  rownames(net.metrics) <- c("num.edges","num.vertices","connectedness","connectance","average.degree","average.path.length","diameter",
                             "edge_connectivity","vertex.connectivity","cohesion","clustering.coefficient","no.clusters","avenei","centralization.closeness",
                             "centralization.betweenness","centralization.degree","assortativity.degree","modularity","average.betweenness","w.diameter","no.positive","no.negative")
  colnames(net.metrics) <- k
  #write.csv(net.bac.metrics,"16S.AU50.all.net.metricsHEL.csv")
  print(net.metrics)
  
  net.metrics <- as.data.frame(net.metrics)
  #net.metrics$name <- rownames(net.metrics)
  net.metrics1 <<- net.metrics
  
  # set vertices size
  v.size <- otu2[V(g)$name, ] 
  v.size1 = log(v.size$abu * 100000)  
  V(g)$size =  abs(v.size1)
  
  E.color <-  E(g)$Cor
  E.color = ifelse(E.color > 0, "red",ifelse(E.color < 0, "blue", "grey"))
  E(g)$color = as.character(E.color) 
  
  # color by Vertices/node with Phylum
  V(g)$Phylum <- ID0$Phylum[match(V(g)$name, ID0$OTU.ID)] 
  #V(g)$color <- ID0$color[match(V(g)$name, ID0$OTU.ID)]
  
  E(g)$width = abs(E(g)$Cor)
  
  # title=paste("AMF",k,sep="-")
  name <- c("MC" = "Farmland", "TS" = "Wildland")
  
  set.seed(123)
  p1 <<-  ggraph(g, layout = "nicely") + 
    geom_edge_bend(aes(width = abs(E(g)$Cor), color = E(g)$color),  strength = 0.2) +
    scale_edge_colour_manual(values= c("blue"="blue", "red"="red")) +
    scale_edge_width_continuous(range = c(0.5, 1.2)) +
    geom_node_point(aes(color=factor(V(g)$Phylum), size = V(g)$size)) +
    scale_colour_manual(name="Phylum",values=color) +
    scale_size_continuous(range = c(1,5)) +
    #geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    labs(title=sprintf("Protists-%s",name[k]),
         subtitle =  sprintf("Vertice = %d; Edge = %d", net.metrics["num.vertices",], net.metrics["num.edges",])) +
    guides(edge_colour="none", edge_width="none", size = "none") +
    theme_void() +
    theme(
      plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"), 
      plot.title = element_text(size = 20, face = "bold",hjust=0.5, margin = margin(b = 10)),
      plot.subtitle = element_text(size = 12, face = "bold",hjust=0.5, color="red", margin = margin(b = 10)), 
      legend.title = element_text(colour = "black", size = 15,face = "bold"),
      legend.text = element_text(colour = "black", size = 12,face = "bold"))
  p1
}


protist.network("MC",0.2)
net.metrics <- net.metrics1
p_prot_mc <- p1
protist.network("TS",0.2)
net.metrics$TS <- net.metrics1$TS
p_prot_ts <- p1


property("Protists")
net.metrics_final <- rbind(net.metrics_tmp,net.metrics_fung)

net.metrics_final1 <- net.metrics_final


net.metrics_final1[net.metrics_final1$para =="num.edges" | net.metrics_final1$para =="num.vertices",]$value <- 
  log(net.metrics_final1[net.metrics_final1$para =="num.edges" | net.metrics_final1$para =="num.vertices",]$value)

net.metrics_final1[net.metrics_final1$para =="average.degree" ,]$value <- 
  log(net.metrics_final1[net.metrics_final1$para =="average.degree" ,]$value+1)

net.metrics_final1$para <- factor(net.metrics_final1$para, levels = c("num.edges", 
                                                                    "num.vertices", 
                                                                    "average.degree", 
                                                                    "average.path.length", 
                                                                    "diameter", 
                                                                    "connectance", 
                                                                    "clustering.coefficient", 
                                                                    "modularity"))

net.metrics_final1$group <- factor(net.metrics_final1$group, levels = c("AM fungi", "Prokaryotes", "Fungi", "Protists"))

```{r, fig.align='center',fig.height = 8, fig.width=24, warning=FALSE, message=FALSE}

p_all <- ggplot(net.metrics_final1, aes(x = group, y = value, fill = factor(variable, levels = c("TS","MC")))) +
         geom_col(position = "dodge",width = 0.5) +  # 使用 dodge 来避免柱子重叠
         facet_wrap(~para, scales = "free", nrow = 2, ncol = 4,
             labeller = labeller(para = c(
               num.edges = "Log10(Number of edges)", 
               num.vertices = "Log10(Number of vertices)",  
               average.degree = "Log10(Average degree + 1)", 
               average.path.length = "Average path length",  
               diameter = "Diameter",  
               connectance = "Connectance",  
               clustering.coefficient = "Clustering coefficient",  
               modularity = "Modularity"  
             ))) +  # 按 para 分面，允许各面板尺度不同
         scale_fill_manual(name = "Habitat",
                    values = c("MC" = "#008000","TS" = "#FFA500"),
                    label= c("MC" = "Farmland (Cotton & Maize)","TS" = "Wildland (Tamarix & Suaeda)"),
                    limits = c("TS", "MC")) +
         theme_bw() +
         theme(axis.text.x = element_text(size = 12,color = "black", face = "bold", angle = 15, hjust = 1),
               axis.text.y = element_text(size = 12,color = "black", face = "bold"),
               axis.title = element_blank(),
               strip.text = element_text(size = 10, color = "black", face = "bold"),
               panel.spacing.x = unit(10, "lines"),
               legend.title = element_text(size=16, face = "bold"),
               legend.text = element_text(size = 12, face = "bold"),
               legend.position = c(1.12, 0.5))
p_all

# Set theme for annotations
# thm <- theme(plot.title = element_text(face=2, size = 25))
# 
# top_plot <- wrap_elements((p_amf_ts|p_bac_ts|p_fung_ts|p_prot_ts) + 
#                                plot_annotation(title = "b", theme = thm))
# middle_plot      <- wrap_elements((p_amf_mc|plot_spacer()|p_bac_mc|plot_spacer()|p_fung_mc|p_prot_mc) + 
#                                     plot_layout(widths = c(4, 1 ,4, 0.5, 4, 4)) +
#                                  plot_annotation(title = "a", theme = thm))
# 
# bottom_plot   <- wrap_elements(p_all + plot_annotation(title = "c", theme = thm))
# 
# top_plot / middle_plot /bottom_plot + plot_layout(heights = c(5,5,7))


p_amf_ts <- p_amf_ts + labs(title = "AM fungi-Wildland\n(Tamarix & Suaeda)")
p_amf_mc <- p_amf_mc + labs(title = "AM fungi-Farmland\n(Cotton & Maize)")

p_bac_ts <- p_bac_ts + labs(title = "Prokaryotes-Wildland\n(Tamarix & Suaeda)")
p_bac_mc <- p_bac_mc + labs(title = "Prokaryotes-Farmland\n(Cotton & Maize)")

p_fung_ts <- p_fung_ts + labs(title = "Fungi-Wildland\n(Tamarix & Suaeda)")
p_fung_mc <- p_fung_mc + labs(title = "Fungi-Farmland\n(Cotton & Maize)")

p_prot_ts <- p_prot_ts + labs(title = "Protists-Wildland\n(Tamarix & Suaeda)")
p_prot_mc <- p_prot_mc + labs(title = "Protists-Farmland\n(Cotton & Maize)")

```{r, fig.align='center',fig.height = 15, fig.width=24, warning=FALSE, message=FALSE}

(((p_amf_ts|p_bac_ts|p_fung_ts|p_prot_ts)/(p_amf_mc|p_bac_mc|p_fung_mc|p_prot_mc))/p_all) +plot_layout(heights = c(4,4,6))
#(((p_amf_ts|p_bac_ts|p_fung_ts|p_prot_ts)/(p_amf_mc|p_bac_mc|p_fung_mc|p_prot_mc))/plot_spacer()) +plot_layout(heights = c(4,4,0.5))

# 24 15

```
