---
title: "Fig.S2_Species accumulation"
author: "Huanhuan Zhu"
date: "2024-09-25"
output: html_document
---


```{r,fig.align='center', fig.height=5, fig.width=10}
#############################Fig.S2 Species accumulation##########################

# load package
library(dplyr)  #to use count/everything
library(RColorBrewer)
library(tidyverse)  # %>%
library(reshape2)  # melt
library(patchwork)

### 1.AMF
# set work dictionary
rm(list = ls())
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/AMF/otu")

my_amfbarplot <- function(a, legend, path) {
  
  # set color
  m1 = brewer.pal(9, "Set1")
  m2 = brewer.pal(12, "Set3")
  Palette1 <-
    c("#B2182B","#E69F00","#56B4E9","#009E73","#F0E442","#0072B2","#D55E00",
      "#CC79A7","#CC6666","#9999CC","#66CC99","#999999","#ADD1E5")
  Palette2 <-
    c('blue','orange','green','yellow','red','hotpink','cyan','purple',
      'burlywood1','skyblue','grey','#8b2578','#458b74','#f0ffff','#eeb422',
      '#ee6aa7','#8b3a62','#cd5c5c','#ee6363','#f0e68c','#e6e6fa','#add8e6',
      '#bfefff','#f08080','#d1eeee','#7a8b8b','#8b814c','#8b5f65','gray')
  mix <- c(m1, Palette2, Palette1, m2)
 
  # load otu table
  otu_all0 <- read.csv("otu_amfFlattening.csV", check.names = F,header = T)
  names(otu_all0)[1] <- "OTU.ID"
  
  # load taxonomy infomation and conbine with otu table
  taxa <-read.csv("HMME.amf.OTU.ID1.csv", check.names = F,row.names = 1,header = T)
  otu_all0 <- merge(otu_all0, taxa, by.x = "OTU.ID", by.y = "OTU.ID")
  colnames(otu_all0)
  
  # check the duplicate item
  # count(otu_all0, "genus")
  # count(otu_all0, "family")
  # count(otu_all0, "order")
  # count(otu_all0, "class")
  
  # sum abundance according to certain taxon level
  i = 42 + a
  wx <- otu_all0[, i]
  otu_all0 <- otu_all0[, c(2:26, i)] %>%
    group_by({
      {
        wx
      }
    }) %>%
    summarise(across(1:25, sum))
  
  # remove "g__" before the genus name
  otu_all0$`<chr>` <- gsub("[a-zA-Z]__","",otu_all0$`<chr>`)
  
  # calculate relative abundance
  my_function <- function(x)x / sum(x)
  otu_all <- otu_all0
  otu_all[, 2:26] <- apply(otu_all[, 2:26], 2, my_function)
  
  otu_all <- as.data.frame(otu_all)
  colSums(otu_all[, 2:26])
  rownames(otu_all) <- otu_all[, 1]
  
  # filter species with relative abundance grater than 0.001(0.1%)
  genus_filter <- otu_all[rowMeans(otu_all[, 2:26]) > 0.001, ]
  genus_filter$sum <- rowSums(genus_filter[, 2:26])
  # sum and order to select top10 
  genus_filter <- genus_filter[order(genus_filter$sum, decreasing = TRUE), ]
  genus_top10 <- genus_filter[c(1:10), -ncol(genus_filter)]
  
  # remaining taxon be classfied as Others 
  genus_top10['Others', ][, 2:26] <-1 - colSums(genus_top10[, 2:26])  
  if (length(genus_filter[, 1]) <= 10) {
    genus_top10 <- na.omit(genus_top10)
  }  # if less than ten, remove NA
  
  #set color
  # set last one as grey(others is grey)
  colour <- mix[1:nrow(genus_top10)]
  if (nrow(genus_top10) > 10) {
    colour[length(colour)] <- 'gray'
  }
  
  # make taxon name as factor,long format
  genus_top10$Taxonomy <- factor(rownames(genus_top10), levels = rev(rownames(genus_top10)))
  genus_ttop10 <- melt(genus_top10[, 2:27], id = 'Taxonomy')
  
  # load sample_metadata, combine top10 with group information
  group0 <- read.csv("sample_metadata.csv", header = T)
  group <- na.omit(group0)
  group <- group0[order(group0$sample.id), ]
  
  genus_ttop10 <- merge(genus_ttop10, group, by.x = 'variable', by.y = "sample.id")
  genus_tttop10 <<- aggregate(value ~ Taxonomy + plants,mean,data = genus_ttop10)
  
  p1 <<-
        ggplot(genus_tttop10, aes(factor(plants,levels=c("Bare land","Suaeda","Tamarix chinensis","Cotton","Maize")), 100 * value, fill = Taxonomy)) +
        geom_col(position = 'stack', width = 0.5)  +
        scale_fill_manual(values =  rev(c(colour))) +
      #  scale_x_continuous(breaks = seq(0, 6, 1),expand = c(0.03, 0.03)) +  # The distance between the left and right columns and the axis
        labs(fill = legend) +
        ggtitle("AMF") +
        scale_x_discrete(labels = c(
                                    'Bare land' = "Bareland", 
                                    'Cotton' = "Cotton", 
                                    'Maize' = "Maize", 
                                    'Suaeda' = "Suaeda",
                                    'Tamarix chinensis' = "Tamarix")) +
        scale_y_continuous(expand = c(0, 0)) +
        labs(x = 'Plant', y = 'Relative Abundance(%)') +
        theme_classic() + 
        theme_bw() +
        theme( 
              panel.grid = element_blank(),
              panel.background = element_rect(color = 'black', fill = 'transparent'),
              strip.text = element_text(size = 15),
              panel.spacing.x = unit(0.5, "lines"),
              panel.spacing.y = unit(0.8, "lines"),
              plot.title = element_text(hjust = 0.5, size = 25, face = "bold"),
              axis.text = element_text(size = 15, color= "black", face= "bold"),
              axis.title = element_text(size = 20, face = "bold"),
              axis.title.x = element_blank(),
              legend.title = element_text(hjust = 0.5, size = 20, face = "bold"),
              legend.text = element_text(size = 15, face= "bold"),
              legend.key.size = unit(0.3, "inches"), 
              legend.background = element_blank())
  #if not set value*100 above, percantage can be set using scale_y_continuous(labels = scales::percent)(add %)
  p1
  #ggsave(path, p1, height = 5, width = 8)
}

#my_amfbarplot(0, "Kingdom", "./taxonomy/amf-Kingdom-barplot.pdf")
#my_amfbarplot(1, "Phylum", "./taxonomy/amf-Phylum-barplot.pdf")
my_amfbarplot(2, "Class", "./taxonomy/amf-Class-barplot.pdf")
p_amf_class <- p1
my_amfbarplot(3, "Order", "./taxonomy/amf-Order-barplot.pdf")
my_amfbarplot(4, "Family", "./taxonomy/amf-Family-barplot.pdf")
my_amfbarplot(5, "Genus", "./taxonomy/amf-Genus-barplot.pdf")
genus_tttop10 <- aggregate(value ~ Taxonomy, data = genus_tttop10, FUN = "mean") # to calculate mean value of top taxon, which will be used in article
p_amf_genus <- p1


### 2.Bacteria
rm(list = setdiff(ls(), c("p_amf_class","p_amf_genus")))
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Bacteria/otu")

my_bacbarplot <- function(a, legend, title,path) {
  
  m1 = brewer.pal(9, "Set1")
  m2 = brewer.pal(12, "Set3")
  Palette1 <-
    c("#B2182B","#E69F00","#56B4E9","#009E73","#F0E442","#0072B2","#D55E00",
      "#CC79A7","#CC6666","#9999CC","#66CC99","#999999","#ADD1E5")
  Palette2 <-
    c('blue','orange','green','yellow','red','hotpink','cyan','purple',
      'burlywood1','skyblue','grey','#8b2578','#458b74','#f0ffff','#eeb422',
      '#ee6aa7','#8b3a62','#cd5c5c','#ee6363','#f0e68c','#e6e6fa','#add8e6',
      '#bfefff','#f08080','#d1eeee','#7a8b8b','#8b814c','#8b5f65','gray')
  mix <- c(m1, Palette2, Palette1, m2)
  
  otu_all0 <- read.csv("otu_bacteriaFlattening.csv", check.names = F,header = T)
  names(otu_all0)[1] <- "OTU.ID"
  
  taxa <-read.csv("HMME.bact.OTU.ID1.csv", check.names = F,row.names = 1,header = T)
  otu_all0 <- merge(otu_all0, taxa, by.x = "OTU.ID", by.y = "OTU.ID")
  names(otu_all0)[38:43] <-
    c(
      "Bacteria.phylum",
      "Bacteria.class",
      "Bacteria.order",
      "Bacteria.family",
      "Bacteria.genus",
      "Bacteria.species")
  
  # count(otu_all0, "Bacteria.phylum")
  # count(otu_all0, "Bacteria.class")
  # count(otu_all0, "Bacteria.order")
  # count(otu_all0, "Bacteria.family")
  # count(otu_all0, "Bacteria.genus")
  # count(otu_all0, "Bacteria.species")
  
  i = 38 + a
  wx <- otu_all0[, i]
  otu_all0 <- otu_all0[, c(2:26, i)] %>%
    group_by({
      {
        wx
      }
    }) %>%
    summarise(across(1:25, sum))  
  
  if(a==4)(otu_all0$`<chr>` <- gsub("-","-\n",otu_all0$`<chr>`))
  
  my_function <- function(x) x / sum(x)
  otu_all <- otu_all0
  otu_all[, 2:26] <- apply(otu_all[, 2:26], 2, my_function)
  
  otu_all <- as.data.frame(otu_all)
  colSums(otu_all[, 2:26])
  rownames(otu_all) <- otu_all[, 1]
  
  genus_filter <- otu_all[rowMeans(otu_all[, 2:26]) > 0.001, ]
  genus_filter$sum <- rowSums(genus_filter[, 2:26])
  genus_filter <- genus_filter[order(genus_filter$sum, decreasing = TRUE),]

  if (is.element("_", rownames(genus_filter)[1:10]) == TRUE) {
    dup <- c(1:11)[!c(1:11) %in% which(rownames(genus_filter) == "_")]
    genus_top10 <- genus_filter[dup,-ncol(genus_filter)]
  } else{
    genus_top10 <- genus_filter[c(1:10),-ncol(genus_filter)]
  }

  genus_top10['Others',][, 2:26] <-
    1 - colSums(genus_top10[, 2:26])
  if (length(genus_filter[, 1]) <= 10) {
    genus_top10 <- na.omit(genus_top10)
  }
  
  colour <- mix[1:nrow(genus_top10)]
  if (nrow(genus_top10) > 10) {
    colour[length(colour)] <- 'gray'
  }

  genus_top10$Taxonomy <-factor(rownames(genus_top10), levels = rev(rownames(genus_top10)))
  genus_ttop10 <- melt(genus_top10[, 2:27], id = 'Taxonomy')
  
  group0 <- read.csv("sample_metadata.csv", header = T)
  group <- na.omit(group0)
  group <- group0[order(group0$sample.id), ]
  
  genus_ttop10 <- merge(genus_ttop10, group, by.x = 'variable', by.y = "sample.id")
  genus_tttop10 <<- aggregate(value ~ Taxonomy + plants, mean,data = genus_ttop10)

  p1 <<-
        ggplot(genus_tttop10, aes(factor(plants,levels=c("Bare land","Suaeda","Tamarix chinensis","Cotton","Maize")), 100 * value, fill = Taxonomy,20)) +
        geom_col(position = 'stack', width = 0.5)  +
        scale_fill_manual(values =  rev(c(colour))) +
        #scale_x_continuous(breaks = seq(0, 6, 1),expand = c(0.03, 0.03)) + 
        labs(fill = legend) +
        ggtitle(title) +
        scale_x_discrete(labels = c(
                                    'Bare land' = "Bareland", 
                                    'Cotton' = "Cotton", 
                                    'Maize' = "Maize", 
                                    'Suaeda' = "Suaeda",
                                    'Tamarix chinensis' = "Tamarix")) +
        scale_y_continuous(expand = c(0, 0)) +
        labs(x = 'Plant', y = 'Relative Abundance(%)') +
        theme_classic() + 
        theme_bw() +
        theme(
              panel.grid = element_blank(),
              panel.background = element_rect(color = 'black', fill = 'transparent'),
              strip.text = element_text(size = 15),
              panel.spacing.x = unit(0.5, "lines"),
              panel.spacing.y = unit(0.8, "lines"),
              plot.title = element_text(hjust = 0.5, size = 25, face = "bold"),
              axis.text = element_text(size = 15, color= "black", face= "bold"),
              axis.title = element_text(size = 20, face = "bold"),
              axis.title.x = element_blank(),
              legend.title = element_text(hjust = 0.5, size = 20, face = "bold"),
              legend.text = element_text(size = 15, face= "bold"),
              legend.key.size = unit(0.3, "inches"), 
              legend.background = element_blank())
  p1
  #ggsave(path, p1,height = 5.5, width = 11)
}

my_bacbarplot(0, "Phylum","Bacteria", "./taxonomy/bac-Phylum-barplot.pdf")
p_bac_phylum <- p1
genus_tttop10 <- aggregate(value ~ Taxonomy, data = genus_tttop10, FUN = "mean")
my_bacbarplot(1, "Class", "Bacteria","./taxonomy/bac-Class-barplot.pdf")
my_bacbarplot(2, "Order", "Bacteria","./taxonomy/bac-Order-barplot.pdf")
my_bacbarplot(3, "Family", "Bacteria","./taxonomy/bac-Family-barplot.pdf")
my_bacbarplot(4, "Genus", "Bacteria","./taxonomy/bac-Genus-barplot2.pdf")
p_bac_genus <- p1
my_bacbarplot(5, "Species", "Bacteria","./taxonomy/bac-Species-barplot.pdf")


### 3.Fungi

rm(list = setdiff(ls(), c("p_amf_class", "p_amf_genus", "p_bac_phylum", "p_bac_genus")))

setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Fungi/otu")
my_fungbarplot <- function(a, legend, title) {
  
  m1 = brewer.pal(9, "Set1")
  m2 = brewer.pal(12, "Set3")
  
  Palette1 <-
    c("#B2182B","#E69F00","#56B4E9","#009E73","#F0E442","#0072B2","#D55E00",
      "#CC79A7","#CC6666","#9999CC","#66CC99","#999999","#ADD1E5")
  Palette2 <-
    c('blue','orange','green','yellow','red','hotpink','cyan','purple',
      'burlywood1','skyblue','grey','#8b2578','#458b74','#f0ffff','#eeb422',
      '#ee6aa7','#8b3a62','#cd5c5c','#ee6363','#f0e68c','#e6e6fa','#add8e6',
      '#bfefff','#f08080','#d1eeee','#7a8b8b','#8b814c','#8b5f65','gray')
  mix <- c(m1, Palette2, Palette1, m2)
  
  otu_all0 <- read.csv("otu_fungiFlattening.csv", check.names = F,header = T)
  names(otu_all0)[1] <- "OTU.ID"
  
  taxa <- read.csv("HMME.fung.OTU.ID1.csv", check.names = F,row.names = 1,header = T)
  otu_all0 <- merge(otu_all0, taxa, by.x = "OTU.ID", by.y = "OTU.ID")
  colnames(otu_all0)
  names(otu_all0)[38:43] <-
    c(
      "Fungi.phylum",
      "Fungi.class",
      "Fungi.order",
      "Fungi.family",
      "Fungi.genus",
      "Fungi.species"
    )
  
  # count(otu_all0, Fungi.phylum)
  # count(otu_all0, Fungi.class)
  # count(otu_all0, Fungi.order)
  # count(otu_all0, Fungi.family)
  # count(otu_all0, Fungi.genus)
  # count(otu_all0, Fungi.species)
  
  i = 38 + a
  wx <- otu_all0[, i]
  otu_all0 <- otu_all0[, c(2:26, i)] %>%
    group_by({
      {
        wx
      }
    }) %>%
    summarise(across(1:25, sum))
  
  otu_all0$`<chr>` <- gsub("[a-zA-Z]__","",otu_all0$`<chr>`)
  otu_all0$`<chr>` <- gsub("_gen_Incertae_sedis","",otu_all0$`<chr>`)
  
  my_function <- function(x) x / sum(x)
  otu_all <- otu_all0
  otu_all[, 2:26] <- apply(otu_all[, 2:26], 2, my_function)
  
  otu_all <- as.data.frame(otu_all)
  colSums(otu_all[, 2:26])
  rownames(otu_all) <- otu_all[, 1]
  
  genus_filter <- otu_all[rowMeans(otu_all[, 2:26]) > 0.001, ]
  genus_filter$sum <- rowSums(genus_filter[, 2:26])
  genus_filter <- genus_filter[order(genus_filter$sum, decreasing = TRUE),]

  if (is.element("_", rownames(genus_filter)[1:10]) == TRUE) {
    dup <- c(1:11)[!c(1:11) %in% which(rownames(genus_filter) == "_")]
    genus_top10 <- genus_filter[dup,-ncol(genus_filter)]
  } else{
    genus_top10 <- genus_filter[c(1:10),-ncol(genus_filter)]
  }

  genus_top10['Others',][, 2:26] <-
    1 - colSums(genus_top10[, 2:26])
  if (length(genus_filter[, 1]) <= 10) {
    genus_top10 <- na.omit(genus_top10)
  }
  

  colour <- mix[1:nrow(genus_top10)]
  if (nrow(genus_top10) > 10) {
    colour[length(colour)] <- 'gray'
  }
  
  genus_top10$Taxonomy <-
    factor(rownames(genus_top10), levels = rev(rownames(genus_top10)))
  genus_ttop10 <- melt(genus_top10[, 2:27], id = 'Taxonomy')
  
  group0 <- read.csv("sample_metadata.csv", header = T)
  group <- na.omit(group0)
  group <- group0[order(group0$sample.id), ]
  
  genus_ttop10 <- merge(genus_ttop10, group, by.x = 'variable', by.y = "sample.id")
  
  genus_tttop10 <<- aggregate(value ~ Taxonomy + plants, mean, data = genus_ttop10)

  
  p1 <<-
        ggplot(genus_tttop10, aes(factor(plants,levels=c("Bare land","Suaeda","Tamarix chinensis","Cotton","Maize")), 100 * value, fill = Taxonomy)) +
        geom_col(position = 'stack', width = 0.5)  +
        scale_fill_manual(values =  rev(c(colour))) +
        #scale_x_continuous(breaks = seq(0, 6, 1),expand = c(0.03, 0.03)) +
        labs(fill = legend) +
        ggtitle("Fungi") +
        scale_x_discrete(labels = c(
                                    'Bare land' = "Bareland", 
                                    'Cotton' = "Cotton", 
                                    'Maize' = "Maize", 
                                    'Suaeda' = "Suaeda",
                                    'Tamarix chinensis' = "Tamarix")) +
        scale_y_continuous(expand = c(0, 0)) +
        labs(x = 'Plant', y = 'Relative Abundance(%)') +
        theme_classic() + 
        theme_bw() +
        theme(
              panel.grid = element_blank(),
              panel.background = element_rect(color = 'black', fill = 'transparent'),
              strip.text = element_text(size = 15),
              panel.spacing.x = unit(0.5, "lines"),
              panel.spacing.y = unit(0.8, "lines"),
              plot.title = element_text(hjust = 0.5, size = 25, face = "bold"),
              axis.text = element_text(size = 15, color= "black", face= "bold"),
              axis.title = element_text(size = 20, face = "bold"),
              axis.title.x = element_blank(),
              legend.title = element_text(hjust = 0.5, size = 20, face = "bold"),
              legend.text = element_text(size = 15, face= "bold"),
              legend.key.size = unit(0.3, "inches"), 
              legend.background = element_blank())

  p1
  #ggsave(title, p1, height = 5.5, width = 11)
}

my_fungbarplot(0, "Phylum", "./taxonomy/fung-Phylum-barplot.pdf")
p_fung_phylum <- p1
genus_tttop10 <- aggregate(value ~ Taxonomy, data = genus_tttop10, FUN = "mean")
my_fungbarplot(1, "Class", "./taxonomy/fung-Class-barplot.pdf")
my_fungbarplot(2, "Order", "./taxonomy/fung-Order-barplot.pdf")
my_fungbarplot(3, "Family", "./taxonomy/fung-Family-barplot.pdf")
my_fungbarplot(4, "Genus", "./taxonomy/fung-Genus-barplot.pdf")
p_fung_genus <- p1
my_fungbarplot(5, "Species", "./taxonomy/fung-Species-barplot.pdf")


### 4.Protist
rm(list = setdiff(ls(), c("p_amf_class", "p_amf_genus", "p_bac_phylum", "p_bac_genus","p_fung_phylum", "p_fung_genus")))
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Protist/otu")

my_protbarplot <- function(a, legend, path) {
  
    m1 = brewer.pal(9, "Set1")
    m2 = brewer.pal(12, "Set3")
    
    Palette1 <-
      c("#B2182B","#E69F00","#56B4E9","#009E73","#F0E442","#0072B2","#D55E00",
        "#CC79A7","#CC6666","#9999CC","#66CC99","#999999","#ADD1E5")
    Palette2 <-
      c('blue','orange','green','yellow','red','hotpink','cyan','purple',
        'burlywood1','skyblue','grey','#8b2578','#458b74','#f0ffff','#eeb422',
        '#ee6aa7','#8b3a62','#cd5c5c','#ee6363','#f0e68c','#e6e6fa','#add8e6',
        '#bfefff','#f08080','#d1eeee','#7a8b8b','#8b814c','#8b5f65','gray')
    mix <- c(m1, Palette2, Palette1, m2)
  
  otu_all0 <- read.csv("otu_protistFlattening.csv", check.names = F,header = T)
  names(otu_all0)[1] <- "OTU.ID"
  
  taxa <-read.csv("HMME.prot.OTU.ID1.csv", check.names = F,row.names = 1,header = T)
  otu_all0 <- merge(otu_all0, taxa, by.x = "OTU.ID", by.y = "OTU.ID")
  colnames(otu_all0)
  names(otu_all0)[38:44] <-
    c(
      "Protist.domain",
      "Protist.phylum",
      "Protist.class",
      "Protist.order",
      "Protist.family",
      "Protist.genus",
      "Protist.species"
    )
  
  # count(otu_all0, Protist.domain)
  # count(otu_all0, Protist.phylum)
  # count(otu_all0, Protist.class)
  # count(otu_all0, Protist.order)
  # count(otu_all0, Protist.family)
  # count(otu_all0, Protist.genus)
  # count(otu_all0, Protist.species)
  
  i = 38 + a
  wx <- otu_all0[, i]
  otu_all0 <- otu_all0[, c(2:26, i)] %>%
    group_by({
      {
        wx
      }
    }) %>%
    summarise(across(1:25, sum))
  
  otu_all0$`<chr>` <- gsub("[a-zA-Z]:","",otu_all0$`<chr>`) 
  otu_all0$`<chr>` <- gsub("-","-\n",otu_all0$`<chr>`)
  
  my_function <- function(x) x / sum(x)
  otu_all <- otu_all0
  otu_all[, 2:26] <- apply(otu_all[, 2:26], 2, my_function)
  
  otu_all <- as.data.frame(otu_all)
  colSums(otu_all[, 2:26])
  rownames(otu_all) <- otu_all[, 1]
  
  
  genus_filter <- otu_all[rowMeans(otu_all[, 2:26]) > 0.001, ]
  genus_filter$sum <- rowSums(genus_filter[, 2:26])
  
  genus_filter <-genus_filter[order(genus_filter$sum, decreasing = TRUE), ]
  
  genus_top10 <- genus_filter[c(1:10), -ncol(genus_filter)]
  
  genus_top10['Others', ][, 2:26] <- 1 - colSums(genus_top10[, 2:26])
  if (length(genus_filter[, 1]) <= 10) {
    genus_top10 <- na.omit(genus_top10)
  }
  
  
  colour <- mix[1:nrow(genus_top10)]
  
  if (nrow(genus_top10) > 10) {
    colour[length(colour)] <- 'gray'
  }
  
  
  genus_top10$Taxonomy <- factor(rownames(genus_top10), levels = rev(rownames(genus_top10)))
  genus_ttop10 <- melt(genus_top10[, 2:27], id = 'Taxonomy')
  
  
  group0 <- read.csv("sample_metadata.csv", header = T)
  group <- na.omit(group0)
  group <- group0[order(group0$sample.id), ]
  
  genus_ttop10 <- merge(genus_ttop10, group, by.x = 'variable', by.y = "sample.id")
  genus_tttop10 <<- aggregate(value ~ Taxonomy + plants, mean, data = genus_ttop10)
  
  p1 <<-
        ggplot(genus_tttop10, aes(factor(plants,levels=c("Bare land","Suaeda","Tamarix chinensis","Cotton","Maize")), 100 * value, fill = Taxonomy)) +
        geom_col(position = 'stack', width = 0.5)  +
        scale_fill_manual(values =  rev(c(colour))) +
        #scale_x_continuous(breaks = seq(0, 6, 1),expand = c(0.03, 0.03)) +
        labs(fill = legend) +
        ggtitle("Protists") +
        scale_x_discrete(labels = c(
                                    'Bare land' = "Bareland", 
                                    'Cotton' = "Cotton", 
                                    'Maize' = "Maize", 
                                    'Suaeda' = "Suaeda",
                                    'Tamarix chinensis' = "Tamarix")) +
        scale_y_continuous(expand = c(0, 0)) +
        labs(x = 'Plant', y = 'Relative Abundance(%)') +
        theme_classic() + 
        theme_bw() +
        theme(
              panel.grid = element_blank(),
              panel.background = element_rect(color = 'black', fill = 'transparent'),
              strip.text = element_text(size = 15),
              panel.spacing.x = unit(0.5, "lines"),
              panel.spacing.y = unit(0.8, "lines"),
              plot.title = element_text(hjust = 0.5, size = 25, face = "bold"),
              axis.text = element_text(size = 15, color= "black", face= "bold"),
              axis.title = element_text(size = 20, face = "bold"),
              axis.title.x = element_blank(),
              legend.title = element_text(hjust = 0.5, size = 20, face = "bold"),
              legend.text = element_text(size = 15, face= "bold"),
              legend.key.size = unit(0.3, "inches"), 
              legend.background = element_blank())
  
  p1
  #ggsave(path, p1, height = 5.5, width = 11)
}



my_protbarplot(0, "Domain", "./taxonomy/prot-Domain-barplot.pdf")
my_protbarplot(1, "Phylum", "./taxonomy/prot-Phylum-barplot.pdf")
genus_tttop10 <- aggregate(value ~ Taxonomy, data = genus_tttop10, FUN = "mean")
p_prot_phylum <- p1
my_protbarplot(2, "Class", "./taxonomy/prot-Class-barplot.pdf")
my_protbarplot(3, "Order", "./taxonomy/prot-Order-barplot.pdf")
my_protbarplot(4, "Family", "./taxonomy/prot-Family-barplot.pdf")
my_protbarplot(5, "Genus", "./taxonomy/prot-Genus-barplot.pdf")
p_prot_genus <- p1
my_protbarplot(6, "Species", "./taxonomy/prot-Species-barplot.pdf")


# saveRDS(p_amf_class,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/amf_class.rda")
# saveRDS(p_amf_genus,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/amf_genus.rda")
# saveRDS(p_bac_phylum,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/bac_phylum.rda")
# saveRDS(p_bac_genus,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/bac_genus.rda")
# saveRDS(p_fung_phylum,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/fung_phylum.rda")
# saveRDS(p_fung_genus,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/fung_genus.rda")
# saveRDS(p_prot_phylum,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/prot_phylum.rda")
# saveRDS(p_prot_genus,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/prot_genus.rda")

```{r,fig.align='center', fig.height=20, fig.width=18}

p_all <- ((p_amf_class/p_bac_phylum/p_fung_phylum/p_prot_phylum)|(p_amf_genus/p_bac_genus/p_fung_genus/p_prot_genus)) #+
  # plot_annotation(tag_levels = 'a') &
  # theme(plot.tag = element_text(size = 30, face = "bold"))
p_all

# saveRDS(p_all,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/p_all.rda")
# 
# ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/taxonomy.svg", p_all, height = 20, width = 18)
# ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/taxonomy.pdf", p_all, height = 20, width = 18)

```

```
