---
title: "Fig.S6_MCoIA"
author: "Huanhuan Zhu"
date: "2024-09-25"
output: html_document
---

```{r,fig.align='center', fig.height=4, fig.width=6}

#############################Fig.S6_MCoIA##########################

library(omicade4)
library(vegan)
library(ggplot2)
library(patchwork)


rm(list=ls())
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/AMF/otu/")

# Read OTU table
# scale within each taxon, keeping the origin variances within taxon.
AMF <- read.csv("otu_amfFlattening.csv",row.names = 1)
AMF <- scale(AMF)  
#AMF <- AMF[rowSums(AMF)!=0,]
#AMF <- decostand(AMF,"hellinger")

setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Bacteria/otu/")
Bacteria <- read.csv("otu_bacteriaFlattening.csv",row.names = 1)
Bacteria <- scale(Bacteria)
#Bacteria <- Bacteria[rowSums(Bacteria)!=0,]
#Bacteria <- decostand(Bacteria,"hellinger")

setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Fungi/otu/")
Fungi <- read.csv("otu_fungiFlattening.csv",row.names = 1)
Fungi <- scale(Fungi)
#Fungi <- Fungi[rowSums(Fungi)!=0,]
#Fungi <- decostand(Fungi,"hellinger")

setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Protist/otu/")
Protists <- read.csv("otu_protistFlattening.csv",row.names = 1)
Protists <- scale(Protists)
#Protist <- Protist[rowSums(Protist)!=0,]
#Protist <- decostand(Protist,"hellinger")

SA <- list("AMF"=AMF,"Bacteria"=Bacteria,"Fungi"=Fungi,"Protists"=Protists)

# Evaluating the similarity among different samples by hierarchical cluster analysis
layout(matrix(1:4, 1, 4))
par(mar = c(2, 1, 0.1, 6))
for (df in SA) {
  d <- dist(t(df))
  hcl <- hclust(d)
  dend <- as.dendrogram(hcl)
  plot(dend, horiz = TRUE)
}

# Conducting MCoIA
mcoin <- mcia(SA, cia.nf = 4, cia.scan = FALSE, nsc = TRUE)


# Simple plot
type <- colnames(SA$AMF)
type <- sapply(strsplit(type, split="U"), function(x) x[1])
type

plot(mcoin, axes = 1:2, phenovec = type, sample.lab = FALSE, df.color = 1:4)


# Contribution of each axis
df1 <- as.data.frame(mcoin$mcoa$pseudoeig)
names(df1) <- "eig"
df1$relative <- df1$eig/sum(df1$eig)
df1$number <- 1:nrow(df1)

  
# Contribution of factors on each axis
df2 <- as.data.frame(mcoin$mcoa$cov2)
df2$type <- rownames(df2)

# MCoIA plot
df3 <- as.data.frame(mcoin$mcoa$Tli)
df3$type <- rownames(df3)

# Creating new group
df3$habitat <- substr(df3$type, 1, 2)
df3$taxon <- substr(df3$type, 6, nchar(df3$type))


# plot
# Contribution of each axis
p1 <- ggplot(df1) +
      geom_col(aes(x = factor(number), y = relative), fill="black") +
      labs(x = "MCOA Dimension", y = "% of variation") +
      theme_bw() +
      theme(
        axis.text =element_text(size = 12,color = "black", face = "bold"), 
        axis.title = element_text(size = 15,face = "bold"))
p1

# Contribution of factors on axis 1
p2 <- ggplot(df2) +
  geom_col(aes(x = cov21/df1$eig[1],y = factor(type,levels = c(df2$type[order(df2$cov21,decreasing = F)]))), fill = "black") +
  labs(x = "Contribution to MCOA1", y = "Taxon") +
  #ggtitle("MCOA1(16.5% of the global covariance)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 20),
    axis.text  = element_text(size = 12, color = "black", face = "bold"), 
    axis.title = element_text(size=15, face = "bold"))
p2

# Contribution of factors on axis 2
p3 <- ggplot(df2) +
      geom_col(aes(x=cov22/df1$eig[2],y = factor(type, levels = c(df2$type[order(df2$cov21,decreasing = F)]))), fill = "black") +
      labs(x = "Contribution to MCOA2", y = "Taxon") +
      #ggtitle("MCOA2(10.9% of the global covariance)") +
      theme_bw() +
      theme(
        plot.title = element_text(size = 20),
        axis.text  = element_text(size = 12, color = "black", face = "bold"), 
        axis.title = element_text(size=15, face = "bold"))
p3

# MCoIA plot
p4 <- ggplot(df3) +
      geom_point(size=7,alpha=0.5, aes(x=Axis1,y=Axis2,
                     color=factor(habitat,levels = c("CK","JP","CL","MH","YM")),
                     shape=factor(taxon))) +
      scale_colour_manual(
                          name = "Habitat",
                          label = c(
                                    'CK'='Bareland',
                                    'MH'='Cotton',
                                    'YM'='Maize',
                                    'JP'='Suaeda',
                                    'CL'='Tamarix'),
                          values = c("red","blue","purple","darkgreen","deepskyblue")) +
      guides(color=guide_legend(override.aes=list(shape = 16),order=1),
             shape=guide_legend(override.aes=list(),order=2)) +
      labs(x = "MCOA1(16.5%)",y = "MCOA1(10.9%)", shape="Taxon") +
      theme_bw() +
      theme(
        plot.title = element_text(size = 20, face = "bold",hjust=0.5), 
        legend.title = element_text(colour = "black",size = 15,face = "bold"),
        legend.text = element_text(colour = "black",size = 12,face = "bold"),
        axis.text = element_text(colour = "black",size = 12, face = "bold"),
        axis.title = element_text(colour = "black",size = 15, face = "bold")) 
p4



# saveRDS(p1,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mcoa/MCoA_dimension.rda")
# save(p2,df1,df2, df3, file = "E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mcoa/MCoA_axis1.rda")
# saveRDS(p3,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mcoa/MCoA_axis2.rda")
# saveRDS(p4,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mcoa/MCoA_plot.rda")

```{r,fig.align='center', fig.height=5.8, fig.width=12}

p_all <- ((p4)| ((p1 / p2 / p3)) +
          plot_layout(heights = c(8, 4,4))) +
          plot_layout(width = c(5, 4)) #+
          # plot_annotation(tag_levels = 'a') &
          # theme(plot.tag = element_text(size = 20, face = "bold"))

p_all

# saveRDS(p_all,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mcoa/MCoA_all.rda")

# ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mcoa/MCoA.svg", p_all, height = 5.8, width = 12)
# ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mcoa/MCoA.pdf", p_all, height = 5.8, width = 12)

```

