---
title: "Fig.6 Function traits"
author: "Huanhuan Zhu"
date: "2024-09-25"
output: html_document
---

```{r,fig.align='center', fig.height=8, fig.width=10}
#############################Fig.6 Function traits##########################

library(ggplot2)
library(dplyr)
library(tidyr)
library(agricolae)
library(splitstackshape)
library(patchwork)
library(tibble)
library(psych)
library(reshape2)
library(ggpubr)
library(linkET)
library(agricolae) # kruskal for nonparametric test
library(ggh4x)  # set individual y axis for facet

rm(list=ls())
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Bacteria/otu/gtdb")

# read rarefied otu table
otu_table <- otu_table <- read.csv("../otu_bacteriaFlattening.csv")
otu_table1 <- otu_table %>% separate(X, into = c("First", "Second"), "[.]")

# read result blast
blast <- read.table("blast.uotus.bacteria.gtdb.txt",comment.char = "")  # comment.char = "" 琛ㄧず涓嶅皢#鐪嬩綔娉ㄩ噴瀛楃鑰屽拷鐣ュ悗闈㈢殑鍐呭
blast <- blast[!duplicated(blast$V1),]  # 鍒犻櫎閲嶅鐨刼tu

# read metadata of GTDB
metadata_bac <- read.delim("bac120_metadata_r214.tsv",sep = "\t",header = T)
metadata_arc <- read.delim("ar53_metadata_r214.tsv",sep = "\t",header = T)
metadata <- rbind(metadata_bac,metadata_arc)

# filter the results according to otu table
blast1 <- blast[blast[,1] %in% otu_table1[,1],]

blast1 <- blast1 %>% separate(V5, into = c("First", "Second"), "~")
blast1 <- blast1[!duplicated(blast1$V1),]  # delete duolicate OTUs

# merge results of blast and GTDB metadata
blast2 <- merge(blast1,metadata,by.x = "First",by.y="accession")
otu_table2 <- merge(otu_table1,blast2,by.x = "First",by.y = "V1")


### 1. calculate avergae genome size 
my_gs <- function(name){
  
  otu_table3 <- otu_table2
  otu_table3[,3:27] <- apply(otu_table3[,3:27],2,function(x) x/sum(x))  # percentage by column
  colSums(otu_table3[,3:27])  # check if the sum of each column is equal to 1
  
  # average genome size
  for(i in 3:27){  
    otu_table3[,i] <- otu_table3[,i]*otu_table3[,name]
  }
  
  genomesize_ave <- as.data.frame(colSums(otu_table3[,3:27]))

  genomesize_ave3 <- genomesize_ave
  genomesize_ave3$sample.id <- rownames(genomesize_ave3)
  names(genomesize_ave3)[1] <- "genome_size"
  genomesize_ave3 <<- genomesize_ave3
}

### 2. calculate avergae gc content
my_gc <- function(name){
  
  otu_table3 <- otu_table2
  otu_table3[,3:27] <- apply(otu_table3[,3:27],2,function(x) x/sum(x))  # percentage by column
  colSums(otu_table3[,3:27])  # check if the sum of each column is equal to 1
  
  # gc content
  for(i in 3:27){ 
    otu_table3[,i] <- otu_table3[,i]*otu_table3[,name]
  }
  
  gc_ave <- as.data.frame(colSums(otu_table3[,3:27]))
  
  gc_ave3 <- gc_ave
  gc_ave3$sample.id <- rownames(gc_ave3)
  
  names(gc_ave3)[1] <- "gc_content"
  gc_ave3 <<- gc_ave3
}

my_gs("genome_size")
my_gc("gc_percentage")


### 3. rRNA copy number from rrndb

#rm(list = setdiff(ls(), c("p1", "p2")))
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Bacteria/otu/rrndb/")

blast_rrna <- read.delim("blast.uotus.bacteria.rrndb.all.txt", check.names = F,header = F)
blast_rrna <- blast_rrna[!duplicated(blast_rrna$V1),]

blast_rrna1 <-
  concat.split(
    data = blast_rrna,
    split.col = "V7",
    sep = "[|]",
    drop = TRUE
  )  # use ‰/|‰ for 鈥渱‰

rrndb <- read.delim("rrnDB-5.8.tsv", check.names = F)
names(rrndb)[1] <- "id"
names(rrndb)[12] <- "16S"
blast_rrna2 <- merge(blast_rrna1[, c("V1","V7_2")], rrndb[, c("id","16S")] ,by.x="V7_2", by.y="id")

otu_all0 <- read.csv("../otu_bacteriaFlattening.csv", row.names = 1)
otu_all0 <- as.data.frame(apply(otu_all0,2, function(x) x/sum(x)))
colSums(otu_all0)

otu_all0$id <- rownames(otu_all0)

otu_all1 <-
  concat.split(
    data = otu_all0,
    split.col = "id",
    sep = "\\.",
    drop = TRUE
  )

otu_all1 <- otu_all1[,1:26]

otu_all2 <- as.data.frame(merge(otu_all1,blast_rrna2, by.x="id_1", by.y="V1", all.x = TRUE))


for(i in 2:26){ 
  otu_all2[,i] <- otu_all2[,i] * otu_all2[,"16S"]
}
otu_all2 <- na.omit(otu_all2)

rrna_ave <- as.data.frame(colSums(otu_all2[,2:26]))
rrna_ave3 <- rrna_ave
rrna_ave3$sample.id <- rownames(rrna_ave3)
names(rrna_ave3)[1] <- "rrna"


group <- read.csv("sample_metadata.csv")
group <- na.omit(group)
group$cnratio <- group$tc/group$tn
group$npration <- group$tn/group$tp
group$cpration <- group$tc/group$tp
group$napration <- group$tn/group$avail_p*1000
group$capration <- group$tc/group$avail_p*1000


df_list <- list(genomesize_ave3, gc_ave3, rrna_ave3)
df_list2 <- list(genomesize_ave3, gc_ave3, rrna_ave3,group[,c(1,8:18)])

# use Reduce() to megge multiple dataframe one time
traits <- Reduce(function(x, y) merge(x, y, by = "sample.id"), df_list)
traits <- column_to_rownames(traits,"sample.id")
group2 <- group[,c(1,9:19)]
group2 <- column_to_rownames(group2,"sample.id")

traits <- traits[rownames(group2),]

traits2 <- Reduce(function(x, y) merge(x, y, by = "sample.id"), df_list2)
traits2 <- column_to_rownames(traits2,"sample.id")

corr_matrix <- corr.test(traits,group2, method = 'spearman', adjust = 'BH')  # 鏈ず渚嬩娇鐢? Benjamini 鏍℃ p 鍊?
corr_matrix$r
corr_matrix$p

p1_cor <- qcorrplot(corr_matrix) +
      geom_square() +
      geom_mark(sep = '\n',sig_thres = 0.05, size = 3, color = "white") +
      scale_fill_gradientn(colours = RColorBrewer::brewer.pal(11, "RdBu")) +
      scale_x_discrete(labels = c(
                                  pH = "pH", 
                                  salt_content = "Salt_content (‰)", 
                                  tc = "TC (%)", 
                                  tn = "TN (%)", 
                                  tp = "TP (%)", 
                                  avail_p = "Avail_P (mg/kg)",
                                  cnratio = "TC:TN",
                                  npration = "TN:TP",
                                  cpration = "TC:TP",
                                  napration = "TN:Avail_P",
                                  capration = "TC:Avail_P"), 
                       limit = c("pH","salt_content","tc","tn","tp","avail_p","cnratio","npration","cpration","napration","capration"), 
                       position = "top") +
      scale_y_discrete(labels = c(
        genome_size = "Genome size", 
        gc_content = "GC content",
        rrna = "rRNA copy number "
        ), limit = c("gc_content","rrna","genome_size")) +
      labs(title = "") +
      guides(fill = guide_colorbar(title = "Spearman's Rho")) +
      theme(plot.margin = margin(0,0,0,0, unit = "cm"), 
            #plot.title = element_text(size=20,face = "bold", hjust = 0.5),
            plot.title = element_blank(),
            axis.title.y = element_blank(), 
            axis.text = element_text(size = 12,face = "bold"),
            legend.title = element_text(size = 15,face = "bold"),
            legend.text = element_text(size = 12,face = "bold"))

p1_cor

p2_cor <- qcorrplot(correlate(traits2,method = "spearman"), type = "upper", diag = FALSE) +
      geom_square() +
      geom_mark(sep = '\n',sig_thres = 0.05, size = 3.5, color = "white") +
      scale_fill_gradientn(colours = RColorBrewer::brewer.pal(11, "RdBu")) +
      labs(title = "title") +
      guides(fill = guide_colorbar(title = "Spearman's Rho")) +
      theme(plot.title = element_text(size=20,face = "bold", hjust = 0.5),
            axis.text = element_text(size = 12,face = "bold"),
            legend.title = element_text(size = 15,face = "bold"),
            legend.text = element_text(size = 12,face = "bold"))

p2_cor


traits$id <- substr(rownames(traits), 1, 2)

ST <- with(traits,kruskal(genome_size, id, p.adj = "fdr"))

# extract chi square value and p value of nonparametric test
statis <- as.data.frame(rbind(ST$statistics[,1:2]))

# label significance
statis$sig <- 0
statis[statis$p.chisq < 0.001,]$sig  = rep(" < 0.001",nrow(statis[statis$p.chisq < 0.001,]))
statis[statis$p.chisq > 0.001,]$sig  = paste0(" = ",round(statis[statis$p.chisq > 0.001,]$p.chisq,3))

# create datafarme for geom_text
rp.value <- data.frame(
  label=sprintf("P = %.3e (χ² = %.3g)", 
                statis$p.chisq,statis$Chisq),
  x="CL",
  y=5.9)

# extract letter of Post Hoc Tests
statis1 <- as.data.frame(rbind(ST$groups))
# extract mean of nonparametric test
statis2 <- as.data.frame(rbind(ST$means))

# get ymax for letter of Post Hoc test
p1 <- ggplot(data = traits,aes(y=genome_size,x=factor(id))) +
  stat_boxplot(geom = "errorbar",
               width=0.3)
ymaxdata <- layer_data(p1) 
statis2$ymax <- ymaxdata$ymax

# merge tables
statis1$id <- rownames(statis1)
statis2$id <- rownames(statis2)
statis2 <- merge(statis2,statis1,by="id")

# dataframe for geom_text
multcomp.data <- data.frame(
  abc=factor(statis2$groups),
  x     = statis2$id,
  y     = as.numeric(statis2$ymax/1000000)
)

p_gs <- ggplot(data = traits,aes(y=genome_size/1000000,x=factor(id, levels = c("CK","JP","CL","MH","YM"))))+
        stat_boxplot(geom = "errorbar",
                     width=0.3)+
        #  ymaxdata <- layer_data(p)
        geom_boxplot(width=0.5)+
        #  geom_jitter(size=0.8)+
        scale_x_discrete(labels=c(
          "CK" = "Bareland",
          "JP" = "Suaeda",
          "CL" = "Tamarix",
          "MH" = "Cotton",
          "YM" = "Maize"
        )) +
        labs(x="", y="Mb", title = "Average genome size")+
        geom_text(
          data    = rp.value, mapping = aes(x = x, y = y, label = label),parse = F,  col="red", hjust=0.5,size=5)+ 
        geom_text(data=multcomp.data,aes(x=x,y=y+0.1,label=abc),
                  color="black",
                  size = 6, hjust=0.5)+
        theme_bw()+
        ylim(5,6)+
        theme(panel.grid=element_blank(), 
              axis.ticks.y=element_line(color="black",linewidth=0.5))+
        theme(plot.title = element_text(hjust = 0.5,size=20,face = "bold"),
              axis.title=element_text(size=16,face="bold"),
              axis.title.x = element_blank(),
              axis.text=element_text(size=12,face="bold",color = "black"))
p_gs



ST <- with(traits,kruskal(gc_content, id, p.adj = "fdr"))

# extract results of nonparametric
statis <- as.data.frame(rbind(ST$statistics[,1:2]))

# significance
statis$sig <- 0
statis[statis$p.chisq < 0.001,]$sig  = rep(" < 0.001",nrow(statis[statis$p.chisq < 0.001,]))
statis[statis$p.chisq > 0.001,]$sig  = paste0(" = ",round(statis[statis$p.chisq > 0.001,]$p.chisq,3))

# create dataframe for value 
rp.value <- data.frame(
  label=sprintf("P = %.3e (χ² = %.3g)",  
                statis$p.chisq,statis$Chisq),
  x="CL",
  y=64)

# results of Post Hoc 
statis1 <- as.data.frame(rbind(ST$groups))
statis2 <- as.data.frame(rbind(ST$means))

# get ymax
p1 <- ggplot(data = traits,aes(y=gc_content,x=factor(id)))+ 
  stat_boxplot(geom = "errorbar",
               width=0.3)
ymaxdata <- layer_data(p1) 
statis2$ymax <- ymaxdata$ymax

statis1$id <- rownames(statis1)
statis2$id <- rownames(statis2)
statis2 <- merge(statis2,statis1,by="id")

# dataframe for geom_text
multcomp.data <- data.frame(
  abc=factor(statis2$groups),
  x     = statis2$id,
  y     = as.numeric(statis2$ymax)
)

p_gc <- ggplot(data = traits,aes(y=gc_content,x=factor(id, levels = c("CK","JP","CL","MH","YM"))))+
  stat_boxplot(geom = "errorbar",
               width=0.3)+
  #  ymaxdata <- layer_data(p)
  geom_boxplot(width=0.5)+
  #  geom_jitter(size=0.8)+
  scale_x_discrete(labels=c(
    "CK" = "Bareland",
    "JP" = "Suaeda",
    "CL" = "Tamarix",
    "MH" = "Cotton",
    "YM" = "Maize"
  )) +
  labs(x="", y="%", title = "GC_content")+
  geom_text(
    data    = rp.value, mapping = aes(x = x, y = y, label = label),parse = F,  col="red", hjust=0.5,size=5)+ 
  geom_text(data=multcomp.data,aes(x=x,y=y+0.5,label=abc),
            color="black",
            size = 6, hjust=0.5)+
  theme_bw()+
  ylim(59.5,64.5)+
  theme(panel.grid=element_blank(), 
        axis.ticks.y=element_line(color="black",linewidth=0.5))+
  theme(plot.title = element_text(hjust = 0.5,size=20,face = "bold"),
        axis.title=element_text(size=16,face="bold"),
        axis.title.x = element_blank(),
        axis.text=element_text(size=12,face="bold",color = "black"))
p_gc



ST <- with(traits,kruskal(rrna, id, p.adj = "fdr"))

statis <- as.data.frame(rbind(ST$statistics[,1:2]))

statis$sig <- 0
statis[statis$p.chisq < 0.001,]$sig  = rep(" < 0.001",nrow(statis[statis$p.chisq < 0.001,]))
statis[statis$p.chisq > 0.001,]$sig  = paste0(" = ",round(statis[statis$p.chisq > 0.001,]$p.chisq,3))

rp.value <- data.frame(
  label=sprintf("P = %.3e (χ² = %.3g)",  
                statis$p.chisq,statis$Chisq),
  x="CL",
  y=4.7)


statis1 <- as.data.frame(rbind(ST$groups))
statis2 <- as.data.frame(rbind(ST$means))


p1 <- ggplot(data = traits,aes(y=rrna,x=factor(id)))+
  stat_boxplot(geom = "errorbar",
               width=0.3)
ymaxdata <- layer_data(p1) 
statis2$ymax <- ymaxdata$ymax

statis1$id <- rownames(statis1)
statis2$id <- rownames(statis2)
statis2 <- merge(statis2,statis1,by="id")

multcomp.data <- data.frame(
  abc=factor(statis2$groups),
  x     = statis2$id,
  y     = as.numeric(statis2$ymax)
)

p_rrna <- ggplot(data = traits,aes(y=rrna,x=factor(id, levels = c("CK","JP","CL","MH","YM"))))+
  stat_boxplot(geom = "errorbar",
               width=0.3)+
  #  ymaxdata <- layer_data(p)
  geom_boxplot(width=0.5)+
  #  geom_jitter(size=0.8)+
  scale_x_discrete(labels=c(
    "CK" = "Bareland",
    "JP" = "Suaeda",
    "CL" = "Tamarix",
    "MH" = "Cotton",
    "YM" = "Maize"
  )) +
  labs(x="", y= "",title = "rDNA copy number")+
  geom_text(
    data    = rp.value, mapping = aes(x = x, y = y, label = label),parse = F,  col="red", hjust=0.5,size=5)+ 
  geom_text(data=multcomp.data,aes(x=x,y=y+0.2,label=abc),
            color="black",
            size = 6, hjust=0.5)+
  theme_bw()+
  ylim(2.6,5)+
  theme(panel.grid=element_blank(), 
        axis.ticks.y=element_line(color="black",linewidth=0.5))+
  theme(plot.title = element_text(hjust = 0.5,size=20,face = "bold"),
        axis.title=element_text(size=16,face="bold"),
        axis.title.x = element_blank(),
        axis.text=element_text(size=12,face="bold",color = "black"))
p_rrna



# group
traits3 <- traits[traits$id != "CK",]
traits3[traits3$id == "JP" | traits3$id == "CL",]$id <- "Wildland"
traits3[traits3$id == "YM" | traits3$id == "MH",]$id <- "Farmland"

# t test
test_gs <- wilcox.test(genome_size~id,traits3)
test_gc <- wilcox.test(gc_content~id,traits3)
test_rrna <- wilcox.test(rrna~id,traits3)
#kruskal.test(value~new,genomesize_ave)

traits4 <- melt(traits3, id="id")
traits4[traits4$variable == "genome_size",]$value = traits4[traits4$variable == "genome_size",]$value/1000000
traits4$variable <- factor(traits4$variable, levels=c("genome_size", "rrna", "gc_content"))


dat_text <- data.frame(
  label = c(label=sprintf("P = %.3e (W = %.3g)",  test_gs$p.value,  test_gs$statistic), 
            label=sprintf("P = %.3e (W = %.3g)",  test_gc$p.value,  test_gc$statistic),
            label=sprintf("P = %.3e (W = %.3g)",  test_rrna$p.value,  test_rrna$statistic)),
  variable   = c("genome_size", "gc_content", "rrna"),
  x=c(1.5,1.5,1.5),
  y=c(5.7,62.05,4.65))
dat_text$variable <- factor(dat_text$variable, levels = c("genome_size", "gc_content", "rrna"))

# set individual ylim
scales_y <- list(
  `genome_size` = scale_y_continuous(limits = c(5, 5.8), breaks = seq(5, 6, 0.2)),
  `rrna` = scale_y_continuous(limits = c(2.5, 5), breaks = seq(2.5, 5, 0.6)),
  `gc_content` = scale_y_continuous(limits = c(59.5, 62.5), breaks = seq(59.5, 62.5, 1)))

p_gsgcrrna <- ggplot(traits4,aes(x=factor(id),y=value)) +
  #geom_errorbar() +
  stat_boxplot(geom = "errorbar", width=0.3) +
  geom_boxplot(width=0.5) +
  facet_wrap(.~variable, scales = "free",
             labeller = labeller(variable = c('genome_size' = "Genome size (Mb)",
                                              'rrna' = "rDNA copy number",
                                              'gc_content' = "GC content (%)"))) +
  geom_text(data = dat_text, mapping = aes(x = x, y = y, label = label), parse = F,color ="red") +
  facetted_pos_scales(y = scales_y) +
  theme_bw() +
  theme(panel.grid=element_blank(), 
        axis.ticks.y=element_line(color="black",linewidth=0.5),
        plot.title = element_text(hjust = 0.5,size=20,face = "bold"),
        axis.title = element_blank(),
        strip.text = element_text(size=12,face="bold",color = "black"),
        axis.text=element_text(size=12,face="bold",color = "black"))


p_gsgcrrna


# saveRDS(p1_cor,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/Correlation.rda")
# saveRDS(p2_cor,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/Correlation_all.rda")
# saveRDS(p_gs,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/Genome_size_five.rda")
# saveRDS(p_gc,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/GC_content_five.rda")
# saveRDS(p_rrna,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/rRNA_five.rda")
# saveRDS(p_gsgcrrna,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/GS_GN_rRNA_two.rda")

p_all <- p1_cor / p_gsgcrrna +  plot_layout(heights = c(7, 5)) +
          plot_annotation(tag_levels = 'a') &
          theme(plot.tag = element_text(size = 20, face = "bold"))
p_all

```{r,fig.align='center', fig.height=6, fig.width=15}
p_traits <- p_gs + p_gc + p_rrna
p_traits

# ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/Traits_all_two.svg", p_all, height = 7, width = 10)
# ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/Traits_all_two.pdf", p_all, height = 7, width = 10)
# 
# ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/Traits_five.svg", p_traits, height = 4.5, width = 14)
# ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/Traits_five.pdf", p_traits, height = 4.5, width = 14)


```

