---
title: "Fig.S11_Network density"
author: "Huanhuan Zhu"
date: "2024-09-25"
output: html_document
---

```{r,fig.align='center', fig.height=4, fig.width=6}

#############################Fig.S11_Network density##########################

library(vegan)
library(psych)
library(igraph)
library(beepr)
library(ggplot2)
library(colorRamps)
library(ape)
library(devtools)
library(stringr)
library(reshape2)
library(splitstackshape)
library(emmeans)
library(psych)
library(graphics)
library(phyloseq)
library(dplyr)
library(ggraph)
library(pals)
library(RColorBrewer)
library(patchwork)

### 1. AMF

rm(list=ls())
amf.network<-function(k, para){
  
  # Read OTU table and metadata
  setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/AMF/otu/")
  otu_all <-read.csv("otu_amfFlattening.csv", row.names = 1, check.names = F, header = T)
  
  group <- read.csv("sample_metadata.csv", header = T)
  #group <- na.omit(group)
  
  group_MC <- group %>%
    filter(country == "Uzbekistan",plants=="Maize"|plants=="Cotton")
  group_MC$type <- rep("MC",nrow(group_MC))
  
  group_TS <- group %>%
    filter(country == "Uzbekistan",plants=="Tamarix chinensis"|plants=="Suaeda")
  group_TS$type <- rep("TS",nrow(group_TS))
  
  group2 <- rbind(group_MC,group_TS)
  
  env0 <- group2[order(group2$sample.id), ]
  
  test <- as.data.frame(rowSums(otu_all))
  test$id <- rownames(test)
  test2 <- test[order(test$`rowSums(otu_all)`,decreasing = T),]
  otu_all <- otu_all[test2[test2$`rowSums(otu_all)`>= sum(test2$`rowSums(otu_all)`)*0.000,]$id,]
  
  # Subset data
  env.tmp<-env0[env0$type==k,]
  
  otu_all2 <- otu_all[,colnames(otu_all) %in% env.tmp$sample.id]
  
  # Remove OTU with sequenc less than 5, and occur at least in 2samples 
  otu <- t(otu_all2)[,specnumber(otu_all2) >= ncol(otu_all2)*para & colSums(t(otu_all2)) > 4]
  
  # Calculate correlation
  spman.r0 = corr.test(otu, use="pairwise",method="spearman",adjust="fdr", alpha=.05, ci=FALSE)
  
  # Matrix transform to dataframe
  Cor<-as.matrix(spman.r0$r)  
  
  Cor[lower.tri(Cor)] <- NA  # Keep upper y=triangle
  diag(Cor) <- NA  # Remove diagonal
  Cor.df <- reshape2::melt(Cor, na.rm = TRUE)  # long form
  
  P0<-as.matrix(spman.r0$p)
  
  P0[lower.tri(P0)] <- NA
  diag(P0) <- NA
  P.df <- reshape2::melt(P0, na.rm = TRUE)
  
  df <- merge(Cor.df, P.df, by=c("Var1","Var2"))
  names(df) <- c("row","col","Cor","p")
  df_new <<- data.frame("Cor" = df$Cor, "group" = rep(k,nrow(df)), "mean"=mean(df$Cor))
}

# Creat dataframe for r value
df <- data.frame()
amf.network("MC",0.2)
df <- rbind(df,df_new)
amf.network("TS",0.2)
df <- rbind(df,df_new)

#plot
p_amf <- ggplot(df, aes(x=Cor,color=factor(group))) +
         geom_density(size=1) +
         geom_vline(aes(xintercept=mean,color=factor(group)), linetype= 5, size=1) +
         scale_color_manual(name="Type",values = c("#008000","#FFA500"),
                              labels = c(
                                         "MC"="Farmland", 
                                         "TS"="Wildland")) +
         theme_bw() +
         labs(x="Spearman's Rho", y="Density",title = "AMF") +
         theme(
            plot.title = element_text(size = 20,color = "black",face = "bold", hjust = 0.5), 
            axis.title = element_text(size = 15, face = "bold"),
            axis.text = element_text(colour = "black",size = 12,face = "bold"),
            legend.title = element_text(colour = "black", size = 15, face = "bold"),
            legend.text = element_text(colour = "black", size = 12, face = "bold"),
            legend.spacing = unit(0.1, "cm"))

p_amf


### 2.Bacteria Phylum

rm(list=setdiff(ls(), "p_amf"))
bacteria.network<-function(k, para){
  setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Bacteria/otu/")
  otu_all <-read.csv("otu_bacteriaFlattening.csv", row.names = 1, check.names = F, header = T)
  
  group <- read.csv("sample_metadata.csv", header = T)
  #group <- na.omit(group)
  group_MC <- group %>%
    filter(country == "Uzbekistan",plants=="Maize"|plants=="Cotton")
  group_MC$type <- rep("MC",nrow(group_MC))
  
  group_TS <- group %>%
    filter(country == "Uzbekistan",plants=="Tamarix chinensis"|plants=="Suaeda")
  group_TS$type <- rep("TS",nrow(group_TS))
  
  group2 <- rbind(group_MC,group_TS)
  
  env0 <- group2[order(group2$sample.id), ]
  
  test <- as.data.frame(rowSums(otu_all))
  test$id <- rownames(test)
  test2 <- test[order(test$`rowSums(otu_all)`,decreasing = T),]
  otu_all <- otu_all[test2[test2$`rowSums(otu_all)`>= sum(test2$`rowSums(otu_all)`)*0.000,]$id,]
  
  # Subset data
  env.tmp<-env0[env0$type==k,]
  
  otu_all2 <- otu_all[,colnames(otu_all) %in% env.tmp$sample.id]
  
  otu <- t(otu_all2)[,specnumber(otu_all2) >= ncol(otu_all2)*para & colSums(t(otu_all2)) > 4]
  
  spman.r0 = corr.test(otu, use="pairwise",method="spearman",adjust="fdr", alpha=.05, ci=FALSE)
  
  Cor<-as.matrix(spman.r0$r)  
  
  Cor[lower.tri(Cor)] <- NA
  diag(Cor) <- NA
  Cor.df <- reshape2::melt(Cor, na.rm = TRUE)
  
  P0<-as.matrix(spman.r0$p)
  
  P0[lower.tri(P0)] <- NA
  diag(P0) <- NA
  P.df <- reshape2::melt(P0, na.rm = TRUE)
  
  df <- merge(Cor.df, P.df, by=c("Var1","Var2"))
  names(df) <- c("row","col","Cor","p")
  df_new <<- data.frame("Cor" = df$Cor, "group" = rep(k,nrow(df)), "mean"=mean(df$Cor))
}

df <- data.frame()
bacteria.network("MC",0.2)
df <- rbind(df,df_new)
bacteria.network("TS",0.2)
df <- rbind(df,df_new)

p_bac <-  ggplot(df, aes(x=Cor,color=factor(group))) +
          geom_density(size=1) +
          geom_vline(aes(xintercept=mean,color=factor(group)), linetype= 5, size=1) +
          scale_color_manual(name="Type",values = c("#008000","#FFA500"),
                             labels = c(
                               "MC"="Farmland", 
                               "TS"="Wildland")) +
          theme_bw() +
          labs(x="Spearman's Rho", y="Density",title = "Bacteria") +
          theme(
            plot.title = element_text(size = 20,color = "black",face = "bold", hjust = 0.5), 
            axis.title = element_text(size = 15, face = "bold"),
            axis.text = element_text(colour = "black",size = 12,face = "bold"),
            legend.title = element_text(colour = "black", size = 15, face = "bold"),
            legend.text = element_text(colour = "black", size = 12, face = "bold"),
            legend.spacing = unit(0.1, "cm"))

p_bac

### 3.Fungi

rm(list=setdiff(ls(), c("p_amf","p_bac")))
fungi.network<-function(k, para){
  setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Fungi/otu/")
  otu_all <-read.csv("otu_fungiFlattening.csv", row.names = 1, check.names = F, header = T)
  
  #percent transfer
  data0<-data.frame(t((apply(otu_all,2,function(x){x / sum(x)}))),check.names = FALSE)#2 indicates cols; 鐢熸垚鐨勬槸OTU涓篶ol锛屾牱鍝佷负row
  
  group <- read.csv("sample_metadata.csv", header = T)
  #group <- na.omit(group)
  
  group_MC <- group %>%
    filter(country == "Uzbekistan",plants=="Maize"|plants=="Cotton")
  group_MC$type <- rep("MC",nrow(group_MC))
  
  group_TS <- group %>%
    filter(country == "Uzbekistan",plants=="Tamarix chinensis"|plants=="Suaeda")
  group_TS$type <- rep("TS",nrow(group_TS))
  
  group2 <- rbind(group_MC,group_TS)
  
  env0 <- group2[order(group2$sample.id), ]
  
  test <- as.data.frame(rowSums(otu_all))
  test$id <- rownames(test)
  test2 <- test[order(test$`rowSums(otu_all)`,decreasing = T),]
  otu_all <- otu_all[test2[test2$`rowSums(otu_all)`>= sum(test2$`rowSums(otu_all)`)*0.000,]$id,]
  
  # Subset data
  env.tmp<-env0[env0$type==k,]
  
  otu_all2 <- otu_all[,colnames(otu_all) %in% env.tmp$sample.id]
  
  otu <- t(otu_all2)[,specnumber(otu_all2) >= ncol(otu_all2)*para & colSums(t(otu_all2)) > 4]
  
  spman.r0 = corr.test(otu, use="pairwise",method="spearman",adjust="fdr", alpha=.05, ci=FALSE)
  
  Cor<-as.matrix(spman.r0$r)  
  
  Cor[lower.tri(Cor)] <- NA
  diag(Cor) <- NA
  Cor.df <- reshape2::melt(Cor, na.rm = TRUE)
  
  P0<-as.matrix(spman.r0$p)
  
  P0[lower.tri(P0)] <- NA
  diag(P0) <- NA
  P.df <- reshape2::melt(P0, na.rm = TRUE)
  
  df <- merge(Cor.df, P.df, by=c("Var1","Var2"))
  names(df) <- c("row","col","Cor","p")
  df_new <<- data.frame("Cor" = df$Cor, "group" = rep(k,nrow(df)), "mean"=mean(df$Cor))
}

df <- data.frame()
fungi.network("MC",0.2)
df <- rbind(df,df_new)
fungi.network("TS",0.2)
df <- rbind(df,df_new)


p_fung <- ggplot(df, aes(x=Cor,color=factor(group))) +
          geom_density(size=1) +
          geom_vline(aes(xintercept=mean,color=factor(group)), linetype= 5, size=1) +
          scale_color_manual(name="Type",values = c("#008000","#FFA500"),
                             labels = c(
                               "MC"="Farmland", 
                               "TS"="Wildland")) +
          theme_bw() +
          labs(x="Spearman's Rho", y="Density",title = "Fungi") +
          theme(
            plot.title = element_text(size = 20,color = "black",face = "bold", hjust = 0.5), 
            axis.title = element_text(size = 15, face = "bold"),
            axis.text = element_text(colour = "black",size = 12,face = "bold"),
            legend.title = element_text(colour = "black", size = 15, face = "bold"),
            legend.text = element_text(colour = "black", size = 12, face = "bold"),
            legend.spacing = unit(0.1, "cm"))
p_fung

#########################Protist Phylum########################

rm(list=setdiff(ls(), c("p_amf","p_bac","p_fung")))
protist.network<-function(k, para){
  setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Protist/otu/")
  otu_all <-read.csv("otu_protistFlattening.csv", row.names = 1, check.names = F, header = T)
  
  #percent transfer
  data0<-data.frame(t((apply(otu_all,2,function(x){x / sum(x)}))),check.names = FALSE)#2 indicates cols; 鐢熸垚鐨勬槸OTU涓篶ol锛屾牱鍝佷负row
  
  group <- read.csv("sample_metadata.csv", header = T)
  #group <- na.omit(group)
  
  
  group_MC <- group %>%
    filter(country == "Uzbekistan",plants=="Maize"|plants=="Cotton")
  group_MC$type <- rep("MC",nrow(group_MC))
  
  group_TS <- group %>%
    filter(country == "Uzbekistan",plants=="Tamarix chinensis"|plants=="Suaeda")
  group_TS$type <- rep("TS",nrow(group_TS))
  
  group2 <- rbind(group_MC,group_TS)
  
  env0 <- group2[order(group2$sample.id), ]
  
  test <- as.data.frame(rowSums(otu_all))
  test$id <- rownames(test)
  test2 <- test[order(test$`rowSums(otu_all)`,decreasing = T),]
  otu_all <- otu_all[test2[test2$`rowSums(otu_all)`>= sum(test2$`rowSums(otu_all)`)*0.000,]$id,]
  
  # Subset data
  env.tmp<-env0[env0$type==k,]
  
  otu_all2 <- otu_all[,colnames(otu_all) %in% env.tmp$sample.id]
  
  otu <- t(otu_all2)[,specnumber(otu_all2) >= ncol(otu_all2)*para & colSums(t(otu_all2)) > 4]
  
  spman.r0 = corr.test(otu, use="pairwise",method="spearman",adjust="fdr", alpha=.05, ci=FALSE)
  
  Cor<-as.matrix(spman.r0$r)  
  
  Cor[lower.tri(Cor)] <- NA
  diag(Cor) <- NA
  Cor.df <- reshape2::melt(Cor, na.rm = TRUE)
  
  P0<-as.matrix(spman.r0$p)
  
  P0[lower.tri(P0)] <- NA
  diag(P0) <- NA
  P.df <- reshape2::melt(P0, na.rm = TRUE)
  
  df <- merge(Cor.df, P.df, by=c("Var1","Var2"))
  names(df) <- c("row","col","Cor","p")
  df_new <<- data.frame("Cor" = df$Cor, "group" = rep(k,nrow(df)), "mean"=mean(df$Cor))
}

df <- data.frame()
protist.network("MC",0.5)
df <- rbind(df,df_new)
protist.network("TS",0.5)
df <- rbind(df,df_new)


p_prot <- ggplot(df, aes(x = Cor,color = factor(group))) +
          geom_density(size = 1) +
          geom_vline(aes(xintercept = mean,color = factor(group)), linetype = 5, size = 1) +
          scale_color_manual(name = "Type",values = c("#008000","#FFA500"),
                             labels = c(
                               "MC" = "Farmland", 
                               "TS" = "Wildland")) +
          theme_bw() +
          labs(x="Spearman's Rho", y="Density",title = "Protists") +
          theme(
            plot.title = element_text(size = 20,color = "black",face = "bold", hjust = 0.5), 
            axis.title = element_text(size = 15, face = "bold"),
            axis.text = element_text(colour = "black",size = 12,face = "bold"),
            legend.title = element_text(colour = "black", size = 15, face = "bold"),
            legend.text = element_text(colour = "black", size = 12, face = "bold"),
            legend.spacing = unit(0.1, "cm"))

p_prot


# saveRDS(p_amf,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network_density/network_density_amf_mc.rda")
# saveRDS(p_bac,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network_density/network_density_bac_mc.rda")
# saveRDS(p_fung,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network_density/network_density_fung_mc.rda")
# saveRDS(p_prot,"E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network_density/network_density_prot_mc.rda")

```{r,fig.align='center', fig.height=8, fig.width=12}

p_all <- (p_amf + p_bac + p_fung + p_prot) #+
  # plot_annotation(tag_levels = 'a') &
  # theme(plot.tag = element_text(size = 15, face = "bold"))

p_all


# ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network_density/network_density.svg", p_all, height = 8, width = 12)
# ggsave("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network_density/network_density.pdf", p_all, height = 8, width = 12)


```

