---
title: "Final_plots"
author: "Huanhuan Zhu"
date: "2024-10-23"
output: html_document
---

```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE}

library(figpatch)
library(ggplot2)
library(patchwork)
library(ggtext)
library(Cairo)
library(showtext)
library(igraph)
font_add('TNR_B', regular = 'C:/Windows/Fonts/timesi.ttf ')
font_add('TNR', regular = 'C:/Windows/Fonts/times.ttf ')
# showtext_begin()

```
############################################Fig.1#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=9, fig.width=15}

rm(list=ls())
# map & images
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/map")

site1 <- fig("site1.jpg") 
site2 <- fig("site2.jpg") 
site3 <- fig("site3.jpg") 

map <- readRDS("Map_UZ1.rda")

# physiochemical properties
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/physiochemical properties/")

pH <- readRDS("total_carbon.rda")
salt_content <- readRDS("salt_content.rda")

# remove margin 
site1 <- site1 + theme(plot.margin = margin(0,0,0,0, unit = "cm"))
site2 <- site2 + theme(plot.margin = margin(0,0,0,0, unit = "cm"))
site3 <- site3 + theme(plot.margin = margin(0,0,0,0, unit = "cm"))
map <- map + theme(plot.margin = margin(0,0,0,0, unit = "cm"))
pH <- pH + theme(plot.margin = margin(0,0,0,0, unit = "cm"),
                 axis.text.x = element_text(angle = 20, hjust = 0.7))
salt_content <- salt_content + theme(plot.margin = margin(0,0,0,0, unit = "cm"),
                                     axis.text.x = element_text(angle = 20, hjust = 0.7))

design <- "111111111111111111111111111555555555
           111111111111111111111111111555555555
           111111111111111111111111111555555555
           111111111111111111111111111555555555
           111111111111111111111111111555555555
           111111111111111111111111111555555555
           111111111111111111111111111555555555
           111111111111111111111111111555555555
           111111111111111111111111111555555555
           111111111111111111111111111555555555
           111111111111111111111111111555555555
           111111111111111111111111111666666666
           111111111111111111111111111666666666
           111111111111111111111111111666666666
           222222222333333333444444444666666666
           222222222333333333444444444666666666
           222222222333333333444444444666666666
           222222222333333333444444444666666666
           222222222333333333444444444666666666
           222222222333333333444444444666666666
           222222222333333333444444444666666666"

p_all <-  map + site1 + site2 +site3 + salt_content + pH+ 
  plot_layout(design=design, guides = "collect") +  
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold"))

print(p_all)

```
############################################Fig.2#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=10, fig.width=12}

rm(list=ls())

# alpha
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/alpha/")

alpha_amf <- readRDS("alpha_Shannon_amf.rda")
alpha_bac <- readRDS("alpha_Shannon_bac.rda")

# beta
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/")

beta_amf <- readRDS("betadisper_amf.rda")
beta_bac <- readRDS("betadisper_bac.rda")

# remove margin 
alpha_amf <- alpha_amf + theme(plot.margin = margin(0,0,0,0, unit = "cm"))
alpha_bac <- alpha_bac + theme(plot.margin = margin(0,0,0,0, unit = "cm"))
beta_amf <- beta_amf + theme(plot.margin = margin(0,0,0,0, unit = "cm"))
beta_bac <- beta_bac + theme(plot.margin = margin(0,0,0,0, unit = "cm"))



design <-  "12
            34"

#showtext_begin()
p_all <-  alpha_amf + alpha_bac + beta_amf +beta_bac + 
          plot_layout(design=design, guides = "collect") +  
          plot_annotation(tag_levels = 'a') &
          theme(plot.tag = element_text(size = 25, face = "bold"))

print(p_all)  

```
############################################Fig.3#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=5, fig.width=12}

rm(list=ls())

# icamp
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/icamp/")

icamp_amf <- readRDS("AMF_process.rda")
icamp_bac <- readRDS("Bac_process.rda")

# remove margin 
icamp_amf <- icamp_amf + theme(plot.margin = margin(0,0,0,0, unit = "cm"))
icamp_bac <- icamp_bac + theme(plot.margin = margin(0,0,0,0, unit = "cm"))

design <- "12"

p_all <- icamp_amf + icamp_bac + 
  plot_layout(design=design, guides = c("collect")) +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold")) 

print(p_all) 

```
############################################Fig.4#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=10.5, fig.width=12}

rm(list=ls())

# network & properties
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network/")

amf_mc <- readRDS("network_Shannon_amf_mc.rda")
amf_ts <- readRDS("network_Shannon_amf_ts.rda")

bac_mc <- readRDS("network_Shannon_bac_mc.rda")
bac_ts <- readRDS("network_Shannon_bac_ts.rda")

# remove margin 
amf_ts <- amf_ts + theme(plot.margin = margin(0,0,0,0, unit = "cm")) + labs(title = "AM fungi-Wildland\n(Tamarix & Suaeda)")
amf_mc <- amf_mc + theme(plot.margin = margin(0,0,0,0, unit = "cm")) + labs(title = "AM fungi-Farmland\n(Cotton & Maize)")

bac_ts <- bac_ts + theme(plot.margin = margin(0,0,0,0, unit = "cm")) + labs(title = "Prokaryotes-Wildland\n(Tamarix & Suaeda)")
bac_mc <- bac_mc + theme(plot.margin = margin(0,0,0,0, unit = "cm")) + labs(title = "Prokaryotes-Farmland\n(Cotton & Maize)")

design <- "12
           34"

p_all <-  amf_ts + amf_mc + bac_ts + bac_mc + 
  plot_layout(design=design) +  
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold")) 

print(p_all)

```
############################################Fig.5#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=10, fig.width=15}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/picrust2/")

p_cor <- readRDS("Correlation_with_name.rda")
p_abu <- readRDS("Abundance_barplot.rda")

# remove margin 
p_cor <- p_cor + theme(plot.margin = margin(0,0,0,0, unit = "cm"),plot.title = element_blank())
p_abu <- p_abu + theme(plot.margin = margin(0,0,0,0, unit = "cm"),plot.title = element_blank())

p_all <- p_cor + plot_spacer() + p_abu+ plot_layout(guides = c("collect"), ncol = 3,widths = c(10, -3.2 ,8))+
  plot_annotation(tag_levels = 'a') &
  theme(legend.position = 'right', 
        plot.tag = element_text(size = 25, face = "bold")) 
#p_all[[1]] <- p_all[[1]] + theme(plot.margin = margin(0, 0, 0, 0.5, "cm"))
p_all[[3]] <- p_all[[3]] + theme(axis.title.x = element_text(vjust = 50))
#p_all[[3]] <- p_all[[3]] + theme(axis.title.x = element_text(vjust = 21.5))
#p_all[[4]] <- p_all[[4]] + theme(plot.margin = margin(0, 0, 0, -5, "pt"))
p_all

```
############################################Fig.6#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=12, fig.width=16}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mantel/amf&bac/")
p1_cor <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/Correlation.rda")
p_gs <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/GS_two.rda")
p_gc <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/GC_two.rda")
p_rrna <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/rRNA_two.rda")

# differential analysis
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/diffenertial/")
diff_bac <- readRDS("bac2.rda")

# remove margin 
diff_bac <- diff_bac + theme(plot.margin = margin(0,0,0,0, unit = "cm"), 
                             plot.title = element_blank(),
                             legend.position = c(0.5, -0.2), 
                             legend.box = "horizontal")

set.seed(123)
p_all <- ((p_gs|p_gc|p_rrna) + plot_layout(guides = "collect"))/plot_spacer()/((diff_bac|p1_cor)+plot_layout(widths = c(8,5))) +  plot_layout(heights = c(5, 0,7)) +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold"))
print(p_all)

```
############################################Fig.S1#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=14, fig.width=16}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/physiochemical properties/")

p_ph <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/physiochemical properties/pH.rda")
p_sc <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/physiochemical properties/salt_content.rda")
p_tc <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/physiochemical properties/total_carbon.rda")
p_tn <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/physiochemical properties/total_nitrogen.rda")
p_tp <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/physiochemical properties/total_phosphorus.rda")
p_ap <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/physiochemical properties/available_phosphorus.rda")
p_cnration <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/physiochemical properties/CNratio.rda")
p_cpration <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/physiochemical properties/CPratio.rda")
p_npratio <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/physiochemical properties/NPratio.rda")


p_all <- ( p_ph + p_tp + p_tn + p_ap + 
            p_cnration + p_cpration + p_npratio) + plot_layout(guide="collect") +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 28, face = "bold"))

p_all

```
############################################Fig.S2#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=22, fig.width=20}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/")

p_amf_class <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/amf_class.rda")
p_amf_genus <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/amf_genus.rda")
p_bac_phylum <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/bac_phylum.rda")
p_bac_genus <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/bac_genus.rda")
p_fung_class <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/fung_class.rda")
p_fung_genus <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/fung_genus.rda")
p_prot_phylum <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/prot_phylum.rda")
p_prot_genus <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/taxonomy/prot_genus.rda")

p_all <-  ((p_amf_class+p_amf_genus)/(p_bac_phylum+p_bac_genus)/(p_fung_class+p_fung_genus)/(p_prot_phylum+p_prot_genus)) +
          plot_annotation(tag_levels = 'a') &
          theme(plot.tag = element_text(size = 35, face = "bold"))

p_all

```
############################################Fig.S3#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=15, fig.width=9}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/diffenertial/")

p_amf <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/diffenertial/amf.rda")
p_bac<- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/diffenertial/bac1.rda")
p_prot <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/diffenertial/prot.rda")

p_all <- p_amf/p_bac/p_prot  +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 30, face = "bold"))
p_all


############################################Fig.S4#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=7, fig.width=14}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mcoa/")
load("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mcoa/MCoA_axis1.rda")

p1 <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mcoa/MCoA_dimension.rda")
p3 <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mcoa/MCoA_axis2.rda")
p4 <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mcoa/MCoA_plot.rda")

p_all <- ((p4)| ((p1 / p2 / p3)) +
            plot_layout(heights = c(8.5, 4,4))) +
  plot_layout(width = c(6, 4)) +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 27, face = "bold"))

p_all

```
############################################Fig.S5#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=9.5, fig.width=11.5}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/pcoa/")

p1_amf <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/pcoa/PCoA_amf.rda")
p1_bac <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/pcoa/PCoA_bac.rda")
p1_fung <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/pcoa/PCoA_fung.rda")
p1_prot <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/pcoa/PCoA_prot.rda")

p_all <- (p1_amf + p1_bac + p1_fung + p1_prot) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold"))

p_all

```
############################################Fig.S6#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=10, fig.width=16}

rm(list=ls())

# mantel
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/mantel/")

mantel <- readRDS("all/All.rda")

# remove margin 
mantel <- mantel + theme(plot.margin = margin(0,0,0,0, unit = "cm"))

design <- "1"

p_all <-  mantel +
  plot_layout(design=design)   
  # plot_annotation(tag_levels = 'a') &
  # theme(plot.tag = element_text(size = 28, face = "bold")) 

print(p_all)  

```
############################################Fig.S7#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=9.5, fig.width=11.5}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/rda/")

p2_amf <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/rda/RDA_amf.rda")
p2_bac <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/rda/RDA_bac.rda")
p2_fung <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/rda/RDA_fung.rda")
load("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/rda/RDA_prot.rda")

p_all <- (p2_amf + p2_bac + p2_fung + p2_prot) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold"))

p_all

```
############################################Fig.S8#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=5, fig.width=11}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/alpha/")

p_fung <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/alpha/alpha_Shannon_fung.rda")
p_prot <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/alpha/alpha_Shannon_prot.rda")


p_all <- (p_fung + p_prot) + 
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold"))

p_all

```
############################################Fig.S9#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=13.5, fig.width=11}


rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper//")

p2_amf <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_boxplot_amf.rda")
p2_bac <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_boxplot_bac.rda")
p2_fung <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_boxplot_fung.rda")
p2_prot <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_boxplot_prot.rda")
p3_fung <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_fung.rda")
p3_prot <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/betadisper/betadisper_prot.rda")


#p_all <- ((p2_amf / p3_fung / p3_prot) | ( p2_bac / p2_fung / p2_prot)) + 
p_all <- (((p3_fung | p3_prot) + plot_layout(guides = "collect", heights = 4)) / ((p2_amf | p2_bac) / (p2_fung | p2_prot) + plot_layout(guides = "collect"))) +  
  plot_layout(heights = c(2,5)) +# add tags after bracket
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 24, face = "bold"),
        legend.justification = c(0.5, 0.5))  # adjust position of legend

p_all

```
############################################Fig.S10#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=16, fig.width=9}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/icamp/")

p1_amf <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/icamp/AMF_phy.rda")
p1_bac <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/icamp/Bac_phy.rda")
p1_prot <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/icamp/Prot_phy.rda")

p_all <- (p1_amf / p1_bac / p1_prot) +
  plot_layout(guides = c("collect")) +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold"),
        legend.justification = "left")

p_all

```
############################################Fig.S11#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=5, fig.width=8}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/icamp/")


p2_prot <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/icamp/Prot_process.rda")

p2_prot

```
############################################Fig.S12#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=10.5, fig.width=14}

rm(list=ls())

# network & properties
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network/")

fung_mc <- readRDS("network_Shannon_fung_mc.rda")
fung_ts <- readRDS("network_Shannon_fung_ts.rda")

prot_mc <- readRDS("network_Shannon_prot_mc.rda")
prot_ts <- readRDS("network_Shannon_prot_ts.rda")

# remove margin 
fung_mc <- fung_mc + theme(plot.margin = margin(0,0,0,0, unit = "cm")) + ggtitle("Fungi-Farmland\n(Cotton & Maize)")
fung_ts <- fung_ts + theme(plot.margin = margin(0,0,0,0, unit = "cm")) + ggtitle("Fungi-Wildland\n(Tamarix & Suaeda)")

prot_mc <- prot_mc + theme(plot.margin = margin(0,0,0,0, unit = "cm")) + ggtitle("Protists-Farmland\n(Cotton & Maize)")
prot_ts <- prot_ts + theme(plot.margin = margin(0,0,0,0, unit = "cm")) + ggtitle("Protists-Wildland\n(Tamarix & Suaeda)")

design <- "12
           34"

p_all <-  fung_ts + fung_mc + prot_ts + prot_mc +
  plot_layout(design=design) +  
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold")) 

print(p_all)

```
############################################Fig.S13#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=9, fig.width=12}

rm(list=ls())

# network & properties
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network/")

amf_prop <- readRDS("network_Shannon_amf_prop.rda")
bac_prop <- readRDS("network_Shannon_bac_prop.rda")
fung_prop <- readRDS("network_Shannon_fung_prop.rda")
prot_prop <- readRDS("network_Shannon_prot_prop.rda")

# remove margin 

amf_prop <- amf_prop + theme(plot.margin = margin(0,0,0,0, unit = "cm")) + labs(title = "AM fungi", x=NULL)
bac_prop <- bac_prop + theme(plot.margin = margin(0,0,0,0, unit = "cm")) + labs(title = "Prokaryotes", x=NULL) 
fung_prop <- fung_prop +theme(plot.margin = margin(0,0,0,0, unit = "cm")) + labs(title = "Fungi", x=NULL) 
prot_prop <- prot_prop +theme(plot.margin = margin(0,0,0,0, unit = "cm")) + labs(title = "Protists", x=NULL) 

design <- "12
           34"

p_all <-  amf_prop + bac_prop + fung_prop + prot_prop +
  plot_layout(guides = "collect") + 
  plot_layout(design=design) +  
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold")) 

print(p_all)

```
############################################Fig.S14#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=10, fig.width=13}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network_density//")

p_amf <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network_density/network_density_amf_mc.rda")
p_bac <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network_density/network_density_bac_mc.rda")
p_fung <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network_density/network_density_fung_mc.rda")
p_prot <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/network_density/network_density_prot_mc.rda")

p_all <- (p_amf + p_bac + p_fung + p_prot) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold"))

p_all

```
############################################Fig.S15#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=6.5, fig.width=9}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/picrust2/")

p <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/picrust2/PCoA.rda")

p

```
############################################Fig.S16#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=9, fig.width=18}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/picrust2/supplementary/")

load("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/picrust2/supplementary/all_picrust2_supplementary.rda")
p1 <- p1 + theme(plot.title = element_blank())
p2 <- p2 + theme(plot.title = element_blank())
p3 <- p3 + theme(plot.title = element_blank())

p_all <- p1+p2+p3 + 
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold")) 
print(p_all)


############################################Fig.S7#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=13, fig.width=6.5}

rm(list=ls())

# functional traits
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/")

p_gs <- readRDS("Genome_size_five.rda")
p_gc  <- readRDS("GC_content_five.rda")
p_rrna <- readRDS('rRNA_five.rda')

p_gs <- p_gs + labs(title = "Genome size")
p_gc <- p_gc + labs(title="GC content", y="% GC") + theme(axis.title.y = element_text(size = 16,face = "bold"))

p_all <- p_gs / p_gc / p_rrna +
  plot_layout(guides = "collect") +  
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold")) 
print(p_all)
```

############################################Fig.S18#################################################
```{r, fig.showtext=TRUE,  fig.align='center',warning=FALSE, message=FALSE, fig.height=12, fig.width=5}

rm(list = ls())
setwd("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Bacteria/otu")

p_gs <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/gs_dengsity.rda")
p_gc <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/gc_dengsity.rda")
p_rrna <- readRDS("E:/Saline-alkali soil/Saline-alkali/amplicon/result-U/Figures/traits/rrna_dengsity.rda")

p_all <- p_gs / p_gc / p_rrna +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag = element_text(size = 25, face = "bold")) 

p_all

# showtext_end()
```
